---
title: "Exotic model selection 14"
author: "Lia Ossanna"
date: "2022-05-24"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
options(knitr.kable.NA = "")
library(kableExtra)
library(tidyverse)
library(readxl)
library(metafor)
library(glmulti)
eval(metafor:::.glmulti)
load("ex-modsel.RData")
```

Analysis for Ossanna & Gornish (2022), “Efficacy of labile carbon addition to reduce exotic invasive plants: A review and meta-analysis”, *Journal of Applied Ecology*.

# Introduction
- Model selection follows [this tutorial](https://www.metafor-project.org/doku.php/tips:model_selection_with_glmulti_and_mumin) from the  `metafor` website.
  - Code also adapted from Kinlock 2017 (*Global Ecology and Biogeography*) and Yan 2018 (*Forests*).



## Rationale for moderators included
#### `region`
`region` was selected over `biome` because it gives information redundant to what `region` provides.
```{r}
biome.region <- ex %>% 
  select(region, biome)
biome.region <- unique(biome.region)
count(biome.region, biome)
count(count(biome.region, biome), n)

region.biome <- ex %>% 
  select(biome, region)
region.biome <- unique(region.biome)
count(region.biome, region)
count(count(region.biome, region), n)
```
  - Almost all `biome` levels contain only one `region` level, but the reverse is not true because there are fewer levels of `region`.

`soil_suborder` was excluded because it gives information redundant to what `region` provides.
```{r}
soil.region <- ex %>% 
  select(region, soil_suborder)
soil.region <- unique(soil.region)
count(soil.region, soil_suborder)
count(count(soil.region, soil_suborder), n)

region.soil <- ex %>% 
  select(soil_suborder, region)
region.soil <- unique(region.soil)
count(region.soil, region)
count(count(region.soil, region), n)
```
  - Almost all `soil_suborder` levels contain only one `region` level, but the reverse is not true because there are fewer levels of `region`.
  

#### `dlc`  
- `dlc` was selected in regard to study duration because the single-moderator model analysis revealed it had the highest QM/QT.


#### `C_type`, `cratc`, `plotc`
- `C_type`,  `cratc`, and `plotc` were included because they represent unique and important aspects of a study.
- C rate was converted to categorical version for easier interpretation.

#### `capt`
- `capt` was selected in regard to reapplication because it gives some indication of study duration in combination with `dlc`. 
- The boxplot below shows the relationship between months applying C (`capt`) and total number of C applications (`C_app`).
```{r}
reapp <- ex %>% 
  filter(capt != "1 application total")
ggplot(reapp, aes(x = capt, y = C_app)) +
  geom_boxplot() +
  geom_jitter() +
  theme_bw(base_size = 14) +
  xlab("Months applying C") +
  ylab("Total number of C applications")
```

  - `capt` does not do a very good job of capturing frequency of C applications; studies that applied C over a longer period of time did not necessarily have more frequent applications.


# Setup
```{r, eval=FALSE}
library(tidyverse)
library(metafor)
library(glmulti)

# Load data ---------------------------------------------------------------

raw <- read.csv("data/Table-S2_meta-analysis.csv")
raw$plant_apgfs <- paste(raw$plant_anper, raw$plant_gfs, sep = " ")
raw$C_app_tm <- raw$duration_first - raw$duration_last
raw$C_app_ma <- raw$C_app_tm / raw$C_app

# Data wrangling
trt.cntrl.se.sd <- c("biomass_mean_trt", "biomass_SE_trt", "biomass_SD_trt",
                     "biomass_mean_cntrl", "biomass_SE_cntrl", "biomass_SD_cntrl")
to.drop <- c("biomass_SE_trt", "biomass_SE_cntrl", "to_sd_trt", "to_sd_cntrl")
biomass <- raw %>% 
  select(!(contains("cover"))) %>% 
  select(!contains("density")) %>% 
  filter(!is.na(biomass_mean_trt)) %>% 
  mutate_at(trt.cntrl.se.sd, as.numeric) %>% 
  mutate(to_sd_trt = biomass_SE_trt * sqrt(n_trt)) %>% 
  mutate(to_sd_cntrl = biomass_SE_cntrl * sqrt(n_cntrl)) %>% 
  mutate(biomass_SD_trt = paste(biomass_SD_trt, to_sd_trt)) %>% 
  mutate(biomass_SD_trt = str_remove(biomass_SD_trt, pattern = "NA"), .keep = "unused") %>% 
  mutate(biomass_SD_cntrl = paste(biomass_SD_cntrl, to_sd_cntrl)) %>% 
  mutate(biomass_SD_cntrl = str_remove(biomass_SD_cntrl, pattern = "NA"), .keep = "unused") %>% 
  select(-all_of(to.drop)) %>% 
  mutate_at(c("biomass_SD_trt", "biomass_SD_cntrl"), as.numeric) %>% 
  rename(mean_trt = biomass_mean_trt) %>% 
  rename(mean_cntrl = biomass_mean_cntrl) %>% 
  rename(SD_trt = biomass_SD_trt) %>% 
  rename(SD_cntrl = biomass_SD_cntrl)
biomass$res <- rep("biomass", nrow(biomass))

trt.cntrl.se.sd <- c("cover_mean_trt", "cover_SE_trt", "cover_SD_trt",
                     "cover_mean_cntrl", "cover_SE_cntrl", "cover_SD_cntrl")
to.drop <- c("cover_SE_trt", "cover_SE_cntrl", "to_sd_trt", "to_sd_cntrl")
cover <- raw %>% 
  select(!(contains("biomass"))) %>% 
  select(!contains("density")) %>% 
  filter(!is.na(cover_mean_cntrl)) %>% 
  mutate_at(trt.cntrl.se.sd, as.numeric) %>% 
  mutate(to_sd_trt = cover_SE_trt * sqrt(n_trt)) %>% 
  mutate(to_sd_cntrl = cover_SE_cntrl * sqrt(n_cntrl)) %>% 
  mutate(cover_SD_trt = paste(cover_SD_trt, to_sd_trt)) %>% 
  mutate(cover_SD_trt = str_remove(cover_SD_trt, pattern = "NA"), .keep = "unused") %>% 
  mutate(cover_SD_cntrl = paste(cover_SD_cntrl, to_sd_cntrl)) %>% 
  mutate(cover_SD_cntrl = str_remove(cover_SD_cntrl, pattern = "NA"), .keep = "unused") %>% 
  select(-all_of(to.drop)) %>% 
  mutate_at(c("cover_SD_trt", "cover_SD_cntrl"), as.numeric)  %>% 
  rename(mean_trt = cover_mean_trt) %>% 
  rename(mean_cntrl = cover_mean_cntrl) %>% 
  rename(SD_trt = cover_SD_trt) %>% 
  rename(SD_cntrl = cover_SD_cntrl) # warning because one Burke point is blank (was <1)
cover$res <- rep("cover", nrow(cover))

all.1res <- rbind(biomass, cover)


# Calculating effect size -------------------------------------------------

ex <- all.1res %>%
  filter(str_detect(plant_category, "exotic"))

ex <- escalc(measure = "SMD",
             n1i = n_trt,
             n2i = n_cntrl,
             m1i = mean_trt,
             m2i = mean_cntrl,
             sd1i = SD_trt,
             sd2i = SD_cntrl,
             data = ex)

ex <- ex %>% 
  filter(!is.na(yi)) # 568 to 488 obs



# Categorical versions ----------------------------------------------------

ex$dfc <- c()
for(i in 1:nrow(ex)) {
  if(ex$duration_first[i] == 3) {
    ex$dfc[i] <- "3"
  } else if(between(ex$duration_first[i], 5, 6)) {
    ex$dfc[i] <- "5-6"
  } else if(between(ex$duration_first[i], 7, 12)) {
    ex$dfc[i] <- "7-12"
  } else if(between(ex$duration_first[i], 12, 18)) {
    ex$dfc[i] <- "12-18"
  } else if(between(ex$duration_first[i], 19, 24)) {
    ex$dfc[i] <- "19-24"
  } else if(between(ex$duration_first[i], 25, 36)) {
    ex$dfc[i] <- "25-36"
  } else if(between(ex$duration_first[i], 37, 50)) {
    ex$dfc[i] <- "37-50"
  } else if(between(ex$duration_first[i], 100, 200)) {
    ex$dfc[i] <- "100-200"
  } else {
    ex$dfc[i] <- ">200"
  }
}
ex$dfc <- factor(ex$df, levels = c("3", "5-6", "7-12", "12-18", "19-24", "25-36", "37-50", "100-200", ">200"))

ex$dlc <- c()
for(i in 1:nrow(ex)) {
  if(between(ex$duration_last[i], 0, 1.5)) {
    ex$dlc[i] <- "0-1.5"
  } else if(ex$duration_last[i] == 2) {
    ex$dlc[i] <- "2"
  } else if(between(ex$duration_last[i], 3, 3.5)) {
    ex$dlc[i] <- "3-3.5"
  } else if(between(ex$duration_last[i], 4, 6)) {
    ex$dlc[i] <- "4-6"
  } else if(between(ex$duration_last[i], 7, 12)) {
    ex$dlc[i] <- "7-12"
  } else if(between(ex$duration_last[i], 13, 18)) {
    ex$dlc[i] <- "13-18"
  } else if(between(ex$duration_last[i], 19, 24)) {
    ex$dlc[i] <- "19-24"
  } else if(between(ex$duration_last[i], 36, 49)) {
    ex$dlc[i] <- "36-49"
  } else {
    ex$dlc[i] <- ">100"
  }
}
ex$dlc <- factor(ex$dl, levels = c("0-1.5", "2", "3-3.5", "4-6", "7-12", "13-18", "19-24", 
                                   "36-49", ">100"))

ex$cratc <- c()
for(i in 1:nrow(ex)) {
  if(is.na(ex$C_rate[i])) {
    ex$cratc[i] <- "idk"
  } else if(between(ex$C_rate[i], 0, 100)) {
    ex$cratc[i] <- "30-100"
  } else if(between(ex$C_rate[i], 101, 160)) {
    ex$cratc[i] <- "133-160"
  } else if(between(ex$C_rate[i], 161, 200)) {
    ex$cratc[i] <- "174-200"
  } else if(between(ex$C_rate[i], 201, 300)) {
    ex$cratc[i] <- "210-300"
  } else if(between(ex$C_rate[i], 301, 400)) {
    ex$cratc[i] <- "330-400"
  } else if(between(ex$C_rate[i], 401, 500)) {
    ex$cratc[i] <- "420-500"
  } else if(between(ex$C_rate[i], 501, 600)) {
    ex$cratc[i] <- "506-600"
  } else if(between(ex$C_rate[i], 630, 700)) {
    ex$cratc[i] <- "620-700"
  } else if(between(ex$C_rate[i], 714, 999)) {
    ex$cratc[i] <- "714-999"
  } else if(between(ex$C_rate[i], 1000, 1330)) {
    ex$cratc[i] <- "1000-1330"
  } else if(between(ex$C_rate[i], 1600, 2000)) {
    ex$cratc[i] <- "1600-2000"
  } else if(between(ex$C_rate[i], 2001, 3000)) {
    ex$cratc[i] <- "2110-3000"
  } else if(between(ex$C_rate[i], 3001, 5000)) {
    ex$cratc[i] <- "3346-5000"
  } else {
    ex$cratc[i] <- ">5000"
  }
}
ex$cratc <- factor(ex$cratc, levels = c("30-100", "133-160", "174-200", "210-300", "330-400", "420-500", 
                                        "506-600", "620-700", "714-999", "1000-1330", "1600-2000",
                                        "2110-3000", "3346-5000", ">5000"))

ex$capc <- c()
for(i in 1:nrow(ex)) {
  if(ex$C_app[i] == 1) {
    ex$capc[i] <- "1"
  } else if(ex$C_app[i] == 2) {
    ex$capc[i] <- "2"
  } else if(between(ex$C_app[i], 3, 6)) {
    ex$capc[i] <- "3-6"
  } else if(between(ex$C_app[i], 7, 10)) {
    ex$capc[i] <- "7-10"
  } else if(between(ex$C_app[i], 15, 22)) {
    ex$capc[i] <- "15-22"
  } else if(between(ex$C_app[i], 32, 40)) {
    ex$capc[i] <- "32-40"
  } else {
    ex$capc[i] <- ">40"
  }
}
ex$capc <- factor(ex$capc, levels = c("1", "2", "3-6", "7-10", "15-22", "32-40", ">40"))

ex$capm <- c()
for(i in 1:nrow(ex)) {
  if(ex$C_app_ma[i] == 0) {
    ex$capm[i] <- "1 application total"
  } else if(between(ex$C_app_ma[i], 0.001, 1)) {
    ex$capm[i] <- "<1"
  } else if(between(ex$C_app_ma[i], 1.001, 2)) {
    ex$capm[i] <- "1-2"
  } else if(between(ex$C_app_ma[i], 2.001, 4)) {
    ex$capm[i] <- "2-4"
  } else {
    ex$capm[i] <- "4-11"
  }
}
ex$capm <- factor(ex$capm, levels = c("1 application total", "<1", "1-2", "2-4", "4-11"))

ex$capt <- c()
for(i in 1:nrow(ex)) {
  if(ex$C_app_tm[i] == 0) {
    ex$capt[i] <- "1 application total"
  } else if(between(ex$C_app_tm[i], 0.001, 6)) {
    ex$capt[i] <- "1-6"
  } else if(between(ex$C_app_tm[i], 7, 12)) {
    ex$capt[i] <- "7-12"
  } else if(between(ex$C_app_tm[i], 13, 24)) {
    ex$capt[i] <- "13-24"
  } else if(between(ex$C_app_tm[i], 25, 36)) {
    ex$capt[i] <- "25-36"
  } else if(between(ex$C_app_tm[i], 37, 48)) {
    ex$capt[i] <- "37-48"
  } else {
    ex$capt[i] <- ">48"
  }
}
ex$capt <- factor(ex$capt, levels = c("1 application total", "1-6", "7-12", "13-24", 
                                      "25-36", "37-48", ">48"))

ex$plotc <- c()
for(i in 1:nrow(ex)) {
  if(is.na(ex$plot[i])) {
    ex$plotc[i] <- "idk"
  } else if(ex$plot[i] < 1) {
    ex$plotc[i] <- "<1"
  } else if(ex$plot[i] == 1) {
    ex$plotc[i] <- "1"
  } else if(between(ex$plot[i], 1.3, 3.75)) {
    ex$plotc[i] <- "1.3-3.75"
  } else if(ex$plot[i] == 4) {
    ex$plotc[i] <- "4"
  } else if(between(ex$plot[i], 6, 9)) {
    ex$plotc[i] <- "6-9"
  } else if(ex$plot[i] == 12) {
    ex$plotc[i] <- "12"
  } else if(between(ex$plot[i], 12.5, 16)) {
    ex$plotc[i] <- "12.5-16"
  } else if(ex$plot[i] == 25) {
    ex$plotc[i] <- "25"
  } else if(between(ex$plot[i], 28, 50)) {
    ex$plotc[i] <- "28-50"
  } else if(ex$plot[i] == 75) {
    ex$plotc[i] <- "75"
  } else {
    ex$plotc[i] <- ">100"
  }
}
ex$plotc <- factor(ex$plotc, 
                   levels = c("<1", "1", "1.3-3.75", "4", "6-9", "12", "12.5-16", 
                              "25", "28-50", "75", ">100"))


# Model selection setup ---------------------------------------------------

rma.glmulti <- function(formula, data, V, random,...) {
  do.call("rma.mv", list(as.formula(paste(deparse(formula))), V = as.name(V), random = as.name(random), data = data,  method = "ML", ...))
}
rand <- list(~ 1 | obs_ID, ~ 1 | exp_ID)


# Multimodel inference
eval(metafor:::.glmulti)
```



# 14: `region`, `dlc`, `C_type`, `cratc`, `capt`, `plant_apgfs`, `plotc`
- Model had no outliers.

```{r, eval=FALSE}
ex.ms14 <- ex[!apply(ex[ , c("region", "dlc", "C_type", "cratc", "capt", "plant_apgfs", "plotc")], 1, anyNA), ]

res14 <- glmulti(yi ~ region + dlc + C_type + cratc + capt + plant_apgfs + plotc, 
                  V = "vi", data = ex.ms14, level = 1, fitfunction = rma.glmulti, 
                  random = "rand", crit = "aicc")
```
```{r}
print(res14)

# Models within 2 AICc units
top <- weightable(res14)
top <- top[top$aicc <= min(top$aicc) + 2, ]
top 
plot(res14, type = "s")

# Top 5 models
weightable(res14)[1:5, ]
```

## Top model 1
```{r, fig.width=7, fig.height=7}
summary(res14@objects[[1]])

forest(x = res14@objects[[1]]$b,
       ci.lb = res14@objects[[1]]$ci.lb,
       ci.ub = res14@objects[[1]]$ci.ub,
       slab = rownames(res14@objects[[1]]$b),
       alim = c(-5, 5),
       header = c("Top model 1", "Estimate [95% CI]"),
       cex = 0.75)
```


# Multimodel inference
- Multimodel inference is not necessary because there is only 1 top model (no others within 2 AICc units).