---
title: "Exotic model selection 14"
author: "Lia Ossanna"
date: "11/27/2021"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
options(knitr.kable.NA = "")
library(kableExtra)
library(tidyverse)
library(readxl)
library(metafor)
library(glmulti)
eval(metafor:::.glmulti)
load("../RData/ex-modsel.RData")
```


# Introduction
- This documented differs from previous analysis (`0821_ex_modsel_9.html`) because this `ex` dataset has all density data removed, because density was shown to respond differently than biomass and cover (see "Removing density from exotic dataset" document, `1021_density_rm.html`).
  - I will be using this new no-density dataset (1021 `ex`) over the previous one (0621 `ex`) for all future analysis.
  - Model 14 also has slightly different moderators, `cratc ` (categorical version of C rate) and `plotc` (categorical version of plot size).
- Model selection follows [this tutorial](https://www.metafor-project.org/doku.php/tips:model_selection_with_glmulti_and_mumin) from the  `metafor` website.
  - Code also adapted from Kinlock 2017 (*Global Ecology and Biogeography*) and Yan 2018 (*Forests*).
- 2022-05-26 small update: read in `exotic-cleaned.csv` CSV to replace all the data cleaning and effect size calculation in the beginning.


## Rationale for moderators included
#### `region`
`region` was selected over `biome` because it gives information redundant to what `region` provides.
```{r}
biome.region <- ex %>% 
  select(region, biome)
biome.region <- unique(biome.region)
count(biome.region, biome)
count(count(biome.region, biome), n)

region.biome <- ex %>% 
  select(biome, region)
region.biome <- unique(region.biome)
count(region.biome, region)
count(count(region.biome, region), n)
```
  - Almost all `biome` levels contain only one `region` level, but the reverse is not true because there are fewer levels of `region`.

`soil_suborder` was excluded because it gives information redundant to what `region` provides.
```{r}
soil.region <- ex %>% 
  select(region, soil_suborder)
soil.region <- unique(soil.region)
count(soil.region, soil_suborder)
count(count(soil.region, soil_suborder), n)

region.soil <- ex %>% 
  select(soil_suborder, region)
region.soil <- unique(region.soil)
count(region.soil, region)
count(count(region.soil, region), n)
```
  - Almost all `soil_suborder` levels contain only one `region` level, but the reverse is not true because there are fewer levels of `region`.
  

#### `dlc`  
- `dlc` was selected in regard to study duration because the single-moderator model analysis revealed it had the highest QM/QT.


#### `C_type`, `cratc`, `plotc`
- `C_type`,  `cratc`, and `plotc` were included because they represent unique and important aspects of a study.
- C rate was converted to categorical version for easier interpretation.

#### `capt`
- `capt` was selected in regard to reapplication because it gives some indication of study duration in combination with `dlc`. 
- The boxplot below shows the relationship between months applying C (`capt`) and total number of C applications (`C_app`).
```{r}
reapp <- ex %>% 
  filter(capt != "1 application total")
ggplot(reapp, aes(x = capt, y = C_app)) +
  geom_boxplot() +
  geom_jitter() +
  theme_bw(base_size = 14) +
  xlab("Months applying C") +
  ylab("Total number of C applications")
```

  - `capt` does not do a very good job of capturing frequency of C applications; studies that applied C over a longer period of time did not necessarily have more frequent applications.


# Setup
```{r, eval=FALSE}
library(tidyverse)
library(readxl)
library(metafor)
library(glmulti)

# Load data ---------------------------------------------------------------

ex <- read.csv("data/cleaned/exotic-cleaned.csv") # data cleaning and effect size calculation in separate script


# Model selection setup ---------------------------------------------------

rma.glmulti <- function(formula, data, V, random,...) {
  do.call("rma.mv", list(as.formula(paste(deparse(formula))), V = as.name(V), random = as.name(random), data = data,  method = "ML", ...))
}
rand <- list(~ 1 | obs_ID, ~ 1 | exp_ID)


# Multimodel inference
eval(metafor:::.glmulti)
```



# 14: `region`, `dlc`, `C_type`, `cratc`, `capt`, `plant_apgfs`, `plotc`
- Model had no outliers.

```{r, eval=FALSE}
ex.ms14 <- ex[!apply(ex[ , c("region", "dlc", "C_type", "cratc", "capt", "plant_apgfs", "plotc")], 1, anyNA), ]

res14 <- glmulti(yi ~ region + dlc + C_type + cratc + capt + plant_apgfs + plotc, 
                  V = "vi", data = ex.ms14, level = 1, fitfunction = rma.glmulti, 
                  random = "rand", crit = "aicc")
```
```{r}
print(res14)

# Models within 2 AICc units
top <- weightable(res14)
top <- top[top$aicc <= min(top$aicc) + 2, ]
top 
plot(res14, type = "s")

# Top 5 models
weightable(res14)[1:5, ]
```

## Top model 1
```{r, fig.width=7, fig.height=7}
summary(res14@objects[[1]])

forest(x = res14@objects[[1]]$b,
       ci.lb = res14@objects[[1]]$ci.lb,
       ci.ub = res14@objects[[1]]$ci.ub,
       slab = rownames(res14@objects[[1]]$b),
       alim = c(-5, 5),
       header = c("Top model 1", "Estimate [95% CI]"),
       cex = 0.75)
```

## Top model 1, no intercept
```{r, eval=FALSE}
ex.mv.ms14.ni <- rma.mv(yi = yi,
                     V = vi,
                     random = ~ 1 | exp_ID / obs_ID,
                     data = ex.ms14,
                     mods = ~ dlc + plotc + region + plant_apgfs - 1)
```

```{r, fig.width=7, fig.height=7}
summary(ex.mv.ms14.ni)

forest(x = ex.mv.ms14.ni$b,
       ci.lb = ex.mv.ms14.ni$ci.lb,
       ci.ub = ex.mv.ms14.ni$ci.ub,
       slab = rownames(ex.mv.ms14.ni$b),
       alim = c(-5, 5),
       header = c("Top model 1, no intercept", "Estimate [95% CI]"),
       cex = 0.75)
```


# Multimodel inference
- Multimodel inference is not necessary because there is only 1 top model (no others within 2 AICc units).