---
title: "Exotic single moderator models"
author: "Lia Ossanna"
date: "`r format(Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
---
```{r, include=FALSE, message=FALSE}
library(tidyverse)
library(metafor)
load("../RData/ex-1mod.RData")
```


Analysis for Ossanna & Gornish (2022), “Efficacy of labile carbon addition to reduce exotic invasive plants: A review and meta-analysis”, *Journal of Applied Ecology*.

# Introduction
- This is the analysis of the summary effect and effect of a single moderator on exotic plant abundance.
  - See "Data cleaning and effect size" document for code for data cleaning and calculation of effect size (`pub_data-cleaning.html`).
- For each model there are the model results, proportion of heterogeneity explained by the model ($\frac{Q_M}{Q_E+Q_M}$), and a forest plot.
- When there are missing data for a moderator, a new model is run with the subset of data that the single-moderator model uses; this is reflected in the forest plot.
  - Missing data will return `TRUE` for the first line of code, `any(is.na(dat$variable))`.
- Analysis includes a model run with all the data, and a model run with outliers removed (see "Exotic outliers for models" document for details; `pub_ex-outliers.html`).
  - When only one model is presented, no outliers were removed.


# Setup
```{r, eval=FALSE}
library(tidyverse)
library(metafor)

# Load data ---------------------------------------------------------------

ex <- read.csv("data/cleaned/exotic-cleaned.csv") # data cleaning and effect size calculation in separate script

# Functions ---------------------------------------------------------------

single.mod.cat <- function(dat, var, dat.mv, dat.mv.var, h) {
  print(dat.mv.var)
  print(noquote(paste("QM/QT =", dat.mv.var[["QM"]] / sum(dat.mv.var[["QE"]], dat.mv.var[["QM"]]))))
  
  n.forest <- count(dat, !!sym(var))
  colnames(n.forest) <- c("moderator", "n")
  n.forest$end <- rep(")", dim(n.forest)[1])
  n.forest$n <- paste(n.forest$n, n.forest$end, sep = "")
  n.forest$start <- rep("(n = ", dim(n.forest)[1])
  n.forest$n <- paste(n.forest$start, n.forest$n)
  n.forest$var_col <- paste(n.forest$moderator, n.forest$n)
  n.forest <- n.forest %>% 
    filter(!is.na(moderator))
  overall <- paste("Overall (n = ", dat.mv$k, ")", sep = "")
  
  forest(x = c(dat.mv[[1]], dat.mv.var[[1]]),
         ci.lb = c(dat.mv[[6]], dat.mv.var[[6]]),
         ci.ub = c(dat.mv[[7]], dat.mv.var[[7]]),
         slab = c(overall, n.forest$var_col),
         header = h,
         cex = 0.7)


outliers <- function(dat, out) {
  dat %>% 
    filter(!obs_ID %in% out)
}

# Outliers ----------------------------------------------------------------

out <- c(457, 601)
out.reg <- c(601, 457)
out.dfc <- c(457)
out.crat <- c(54, 120, 132)
out.cratc <- c(437)
out.capm <- c(257, 247, 601)
out.pgfs <- c(257, 258)
```


# No moderators (summary effect)
## All data
```{r, eval=FALSE}
ex.mv <- rma.mv(yi = yi,
                V = vi,
                random = ~ 1 | exp_ID / obs_ID,
                data = ex)
```
```{r}
print(ex.mv)
predict(ex.mv)
ex.mv[["QM"]] / sum(ex.mv[["QE"]], ex.mv[["QM"]])

# I^2
W <- diag(1 / ex$vi)
X <- model.matrix(ex.mv)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
100 * sum(ex.mv$sigma2) / (sum(ex.mv$sigma2) + (ex.mv$k-ex.mv$p)/sum(diag(P)))

100 * ex.mv$sigma2 / (sum(ex.mv$sigma2) + (ex.mv$k-ex.mv$p)/sum(diag(P)))
```

## Outliers removed
```{r, eval=FALSE}
out <- c(457, 601)
ex.o <- outliers(ex, out)
ex.mv.o <- rma.mv(yi = yi,
                  V = vi,
                  random = ~ 1 | exp_ID / obs_ID,
                  data = ex.o)
```
```{r}
print(ex.mv.o)
predict(ex.mv.o)
ex.mv.o[["QM"]] / sum(ex.mv.o[["QE"]], ex.mv.o[["QM"]])

# I^2
W <- diag(1 / ex.o$vi)
X <- model.matrix(ex.mv.o)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
100 * sum(ex.mv.o$sigma2) / (sum(ex.mv.o$sigma2) + (ex.mv.o$k-ex.mv.o$p)/sum(diag(P)))

100 * ex.mv.o$sigma2 / (sum(ex.mv.o$sigma2) + (ex.mv.o$k-ex.mv.o$p)/sum(diag(P)))
```

## Comparison
- Removing outliers does not change significance.
- Removing outliers increases QM/QT, but decreases *I^2^*.

# Biome
```{r}
any(is.na(ex$biome)) # if TRUE, run no-moderators model on subset with no missing data for that moderator (i.e. ex.mv.bio.na)
```
```{r, eval=FALSE}
ex.bio.na <- ex %>% 
  filter(!is.na(biome))

ex.mv.bio <- rma.mv(yi = yi,
                    V = vi,
                    random = ~ 1 | exp_ID / obs_ID,
                    data = ex.bio.na,
                    mods = ~ factor(biome) - 1)

ex.mv.bio.na <- rma.mv(yi = yi,
                       V = vi,
                       random = ~ 1 | exp_ID / obs_ID,
                       data = ex.bio.na)
```
```{r}
h <- c("Biome", "Estimate [95% CI]")
single.mod.cat(ex, "biome", ex.mv.bio.na, ex.mv.bio, h)
```


# Region
## All data
```{r}
any(is.na(ex$region)) # if FALSE, use ex.mv for no-moderator model
  # but still requires new model for outliers removed and levels n > 3
```
```{r, eval=FALSE}
ex.mv.reg <- rma.mv(yi = yi,
                    V = vi,
                    random = ~ 1 | exp_ID / obs_ID,
                    data = ex,
                    mods = ~ factor(region) - 1)
```
```{r}
h <- c("Region (all)", "Estimate [95% CI]")
single.mod.cat(ex, "region", ex.mv, ex.mv.reg, h)
```

## Outliers removed
```{r, eval=FALSE}
out.reg <- c(601, 457)
ex.reg.o <- outliers(ex, out.reg.1)
ex.mv.reg.o <- rma.mv(yi = yi,
                       V = vi,
                       random = ~ 1 | exp_ID / obs_ID,
                       data = ex.reg.o,
                       mods = ~ factor(region) - 1)

ex.mv.reg.na.o <- rma.mv(yi = yi,
                          V = vi,
                          random = ~ 1 | exp_ID / obs_ID,
                          data = ex.reg.o)
```
```{r}
h <- c("Region (outliers removed)", "Estimate [95% CI]")
single.mod.cat(ex.reg.o, "region", ex.mv.reg.na.o, ex.mv.reg.o, h)
```

## Comparison
- Removing outliers does not change significance.
- Removing outliers increases QM/QT.



# Soil suborder
```{r}
any(is.na(ex$soil_suborder))
```
```{r, eval=FALSE}
ex.soil.na <- ex %>% 
  filter(!is.na(soil_suborder))

ex.mv.soil <- rma.mv(yi = yi,
                    V = vi,
                    random = ~ 1 | exp_ID / obs_ID,
                    data = ex.soil.na,
                    mods = ~ factor(soil_suborder) - 1)

ex.mv.soil.na <- rma.mv(yi = yi,
                        V = vi,
                        random = ~ 1 | exp_ID / obs_ID,
                        data = ex.soil.na)
```
```{r}
h <- c("Soil suborder", "Estimate [95% CI]")
single.mod.cat(ex, "soil_suborder", ex.mv.soil.na, ex.mv.soil, h)
```




# Duration since first C app (categorical)
## All data
```{r}
# Create categories
count(ex, duration_first)
```
```{r, eval=FALSE}
ex$dfc <- NA
for(i in 1:nrow(ex)) {
  if(ex$duration_first[i] == 3) {
    ex$dfc[i] <- "3"
  } else if(between(ex$duration_first[i], 5, 6)) {
    ex$dfc[i] <- "5-6"
  } else if(between(ex$duration_first[i], 7, 12)) {
    ex$dfc[i] <- "7-12"
  } else if(between(ex$duration_first[i], 13, 18)) {
    ex$dfc[i] <- "13-18"
  } else if(between(ex$duration_first[i], 19, 24)) {
    ex$dfc[i] <- "19-24"
  } else if(between(ex$duration_first[i], 25, 36)) {
    ex$dfc[i] <- "25-36"
  } else if(between(ex$duration_first[i], 37, 50)) {
    ex$dfc[i] <- "37-50"
  } else if(between(ex$duration_first[i], 100, 200)) {
    ex$dfc[i] <- "100-200"
  } else {
    ex$dfc[i] <- ">200"
  }
}
ex$dfc <- factor(ex$df, levels = c("3", "5-6", "7-12", "12-18", "19-24", "25-36", "37-50", "100-200", ">200"))
```
```{r}
count(ex, dfc)

any(is.na(ex$dfc))
```
```{r, eval=FALSE}
ex.mv.dfc <- rma.mv(yi = yi,
                    V = vi,
                    random = ~ 1 | exp_ID / obs_ID,
                    data = ex,
                    mods = ~ factor(dfc) - 1)
```
```{r}
h <- c("Duration since first C app (all)", "Estimate [95% CI]")
single.mod.cat(ex, "dfc", ex.mv, ex.mv.dfc, h)
```

## Outliers removed
```{r, eval=FALSE}
out.dfc <- c(457)
ex.dfc.o <- outliers(ex, out.dfc)
ex.mv.dfc.o <- rma.mv(yi = yi,
                      V = vi,
                      random = ~ 1 | exp_ID / obs_ID,
                      data = ex.dfc.o,
                      mods = ~ factor(dfc) - 1)

ex.mv.dfc.na.o <- rma.mv(yi = yi,
                         V = vi,
                         random = ~ 1 | exp_ID / obs_ID,
                         data = ex.dfc.o)
```
```{r}
h <- c("Duration since first C app (outliers removed)", "Estimate [95% CI]")
single.mod.cat(ex.dfc.o, "dfc", ex.mv.dfc.na.o, ex.mv.dfc.o, h)
```

## Comparison
- Removing outliers does not change significance.
- Removing outliers increases QM/QT.




# Duration since last C app (categorical)
```{r}
# Create categories
count(ex, duration_last)
```
```{r, eval=FALSE}
ex$dlc <- NA
for(i in 1:nrow(ex)) {
  if(between(ex$duration_last[i], 0, 1.5)) {
    ex$dlc[i] <- "0-1.5"
  } else if(ex$duration_last[i] == 2) {
    ex$dlc[i] <- "2"
  } else if(between(ex$duration_last[i], 3, 3.5)) {
    ex$dlc[i] <- "3-3.5"
  } else if(between(ex$duration_last[i], 4, 6)) {
    ex$dlc[i] <- "4-6"
  } else if(between(ex$duration_last[i], 7, 12)) {
    ex$dlc[i] <- "7-12"
  } else if(between(ex$duration_last[i], 13, 18)) {
    ex$dlc[i] <- "13-18"
  } else if(between(ex$duration_last[i], 19, 24)) {
    ex$dlc[i] <- "19-24"
  } else if(between(ex$duration_last[i], 36, 49)) {
    ex$dlc[i] <- "36-49"
  } else {
    ex$dlc[i] <- ">100"
  }
}
ex$dlc <- factor(ex$dl, levels = c("0-1.5", "2", "3-3.5", "4-6", "7-12", "13-18", "19-24", 
                                   "36-49", ">100"))
```
```{r}
count(ex, dlc)

any(is.na(ex$dlc))
```
```{r, eval=FALSE}
ex.mv.dlc <- rma.mv(yi = yi,
                    V = vi,
                    random = ~ 1 | exp_ID / obs_ID,
                    data = ex,
                    mods = ~ factor(dlc) - 1)
```
```{r}
h <- c("Duration since last C app", "Estimate [95% CI]")
single.mod.cat(ex, "dlc", ex.mv, ex.mv.dlc, h)
```



# C type 
```{r}
any(is.na(ex$C_type))
```
```{r, eval=FALSE}
ex.mv.ctyp <- rma.mv(yi = yi,
                    V = vi,
                    random = ~ 1 | exp_ID / obs_ID,
                    data = ex,
                    mods = ~ factor(C_type) - 1)
```
```{r}
h <- c("C_type", "Estimate [95% CI]")
single.mod.cat(ex, "C_type", ex.mv, ex.mv.ctyp, h)
```


# C rate (categorical)
## All data
```{r}
# Create categories
count(ex, C_rate)
```
```{r, eval=FALSE}
ex$cratc <- NA
for(i in 1:nrow(ex)) {
  if(is.na(ex$C_rate[i])) {
    ex$cratc[i] <- "idk"
  } else if(between(ex$C_rate[i], 0, 100)) {
    ex$cratc[i] <- "30-100"
  } else if(between(ex$C_rate[i], 101, 160)) {
    ex$cratc[i] <- "133-160"
  } else if(between(ex$C_rate[i], 161, 200)) {
    ex$cratc[i] <- "174-200"
  } else if(between(ex$C_rate[i], 201, 300)) {
    ex$cratc[i] <- "210-300"
  } else if(between(ex$C_rate[i], 301, 400)) {
    ex$cratc[i] <- "330-400"
  } else if(between(ex$C_rate[i], 401, 500)) {
    ex$cratc[i] <- "420-500"
  } else if(between(ex$C_rate[i], 501, 600)) {
    ex$cratc[i] <- "506-600"
  } else if(between(ex$C_rate[i], 630, 700)) {
    ex$cratc[i] <- "620-700"
  } else if(between(ex$C_rate[i], 714, 999)) {
    ex$cratc[i] <- "714-999"
  } else if(between(ex$C_rate[i], 1000, 1330)) {
    ex$cratc[i] <- "1000-1330"
  } else if(between(ex$C_rate[i], 1600, 2000)) {
    ex$cratc[i] <- "1600-2000"
  } else if(between(ex$C_rate[i], 2001, 3000)) {
    ex$cratc[i] <- "2110-3000"
  } else if(between(ex$C_rate[i], 3001, 5000)) {
    ex$cratc[i] <- "3346-5000"
  } else {
    ex$cratc[i] <- ">5000"
  }
}
ex$cratc <- factor(ex$cratc, levels = c("30-100", "133-160", "174-200", "210-300", "330-400", "420-500", 
                                     "506-600", "620-700", "714-999", "1000-1330", "1600-2000",
                                     "2110-3000", "3346-5000", ">5000"))
```
```{r}
count(ex, cratc)

any(is.na(ex$cratc))
```
```{r, eval=FALSE}
ex.cratc.na <- ex %>% 
  filter(!is.na(cratc))

ex.mv.cratc <- rma.mv(yi = yi,
                     V = vi,
                     random = ~ 1 | exp_ID / obs_ID,
                     data = ex.cratc.na,
                     mods = ~ factor(cratc) - 1)

ex.mv.cratc.na <- rma.mv(yi = yi,
                        V = vi,
                        random = ~ 1 | exp_ID / obs_ID,
                        data = ex.cratc.na)
```
```{r}
h <- c("C rate (all)", "Estimate [95% CI]")
single.mod.cat(ex.cratc.na, "cratc", ex.mv.cratc.na, ex.mv.cratc, h)
```

## Outliers removed
```{r, eval=FALSE}
out.cratc <- c(437)
ex.cratc.o <- outliers(ex.cratc.na, out.cratc)

ex.mv.cratc.o <- rma.mv(yi = yi,
                      V = vi,
                      random = ~ 1 | exp_ID / obs_ID,
                      data = ex.cratc.o,
                      mods = ~ factor(cratc) - 1)

ex.mv.cratc.na.o <- rma.mv(yi = yi,
                         V = vi,
                         random = ~ 1 | exp_ID / obs_ID,
                         data = ex.cratc.o)
```
```{r}
h <- c("C rate (outliers removed)", "Estimate [95% CI]")
single.mod.cat(ex.cratc.o, "cratc", ex.mv.cratc.na.o, ex.mv.cratc.o, h)
```

## Comparison
- Removing outliers does not change significance.
- Removing outliers increases QM/QT.



# C applications total (categorical)
```{r}
# Create categories
count(ex, C_app)
```
```{r, eval=FALSE}
ex$capc <- NA
for(i in 1:nrow(ex)) {
  if(ex$C_app[i] == 1) {
    ex$capc[i] <- "1"
  } else if(ex$C_app[i] == 2) {
    ex$capc[i] <- "2"
  } else if(between(ex$C_app[i], 3, 6)) {
    ex$capc[i] <- "3-6"
  } else if(between(ex$C_app[i], 7, 10)) {
    ex$capc[i] <- "7-10"
  } else if(between(ex$C_app[i], 15, 22)) {
    ex$capc[i] <- "15-22"
  } else if(between(ex$C_app[i], 32, 40)) {
    ex$capc[i] <- "32-40"
  } else {
    ex$capc[i] <- ">40"
  }
}
ex$capc <- factor(ex$capc, levels = c("1", "2", "3-6", "7-10", "15-22", "32-40", ">40")))
```
```{r}
count(ex, capc)

any(is.na(ex$capc))
```
```{r, eval=FALSE}
ex.mv.capc <- rma.mv(yi = yi,
                     V = vi,
                     random = ~ 1 | exp_ID / obs_ID,
                     data = ex,
                     mods = ~ factor(capc) - 1)
```
```{r}
h <- c("C applications", "Estimate [95% CI]")
single.mod.cat(ex, "capc", ex.mv, ex.mv.capc, h)
```



# Months applying C
```{r}
count(ex, C_app_tm)
```
```{r, eval=FALSE}
ex$capt <- NA
for(i in 1:nrow(ex)) {
  if(ex$C_app_tm[i] == 0) {
    ex$capt[i] <- "1 application total"
  } else if(between(ex$C_app_tm[i], 0.001, 6)) {
    ex$capt[i] <- "1-6"
  } else if(between(ex$C_app_tm[i], 7, 12)) {
    ex$capt[i] <- "7-12"
  } else if(between(ex$C_app_tm[i], 13, 24)) {
    ex$capt[i] <- "13-24"
  } else if(between(ex$C_app_tm[i], 25, 36)) {
    ex$capt[i] <- "25-36"
  } else if(between(ex$C_app_tm[i], 37, 48)) {
    ex$capt[i] <- "37-48"
  } else {
    ex$capt[i] <- ">48"
  }
}
ex$capt <- factor(ex$capt, levels = c("1 application total", "1-6", "7-12", "13-24", 
                                      "25-36", "37-48", ">48"))
```
```{r}
count(ex, capt)

any(is.na(ex$capt))
```
```{r, eval=FALSE}
ex.mv.capt <- rma.mv(yi = yi,
                     V = vi,
                     random = ~ 1 | exp_ID / obs_ID,
                     data = ex,
                     mods = ~ factor(capt) - 1)
```
```{r}
h <- c("Months applying C", "Estimate [95% CI]")
single.mod.cat(ex, "capt", ex.mv, ex.mv.capt, h)
```


# Annual/perennial
```{r}
any(is.na(ex$plant_anper))
```
```{r, eval=FALSE}
ex.mv.panp <- rma.mv(yi = yi,
                     V = vi,
                     random = ~ 1 | exp_ID / obs_ID,
                     data = ex,
                     mods = ~ factor(plant_anper) - 1)
```
```{r}
h <- c("Annual/perennial", "Estimate [95% CI]")
single.mod.cat(ex, "plant_anper", ex.mv, ex.mv.panp, h)
```



# Grass/forb/shrub 
## All data
```{r}
any(is.na(ex$plant_gfs))
```
```{r, eval=FALSE}
ex.mv.pgfs <- rma.mv(yi = yi,
                     V = vi,
                     random = ~ 1 | exp_ID / obs_ID,
                     data = ex,
                     mods = ~ factor(plant_gfs) - 1)
```
```{r}
h <- c("Grass/forb/shrub (all)", "Estimate [95% CI]")
single.mod.cat(ex, "plant_gfs", ex.mv, ex.mv.pgfs, h)
```

## Outliers removed
```{r, eval=FALSE}
out.pgfs <- c(257, 258)
ex.pgfs.o <- outliers(ex, out.pgfs)
ex.mv.pgfs.o <- rma.mv(yi = yi,
                       V = vi,
                       random = ~ 1 | exp_ID / obs_ID,
                       data = ex.pgfs.o,
                       mods = ~ factor(plant_gfs) - 1)

ex.mv.pgfs.na.o <- rma.mv(yi = yi,
                          V = vi,
                          random = ~ 1 | exp_ID / obs_ID,
                          data = ex.pgfs.o)
```
```{r}
h <- c("Grass/forb/shrub (outliers removed)", "Estimate [95% CI]")
single.mod.cat(ex.pgfs.o, "plant_gfs", ex.mv.pgfs.na.o, ex.mv.pgfs.o, h)
```

## Comparison
- Removing outliers changes unknown from significant to not significant.
- Removing outliers increases QM/QT.



# Annual/perennial and grass/forb/shrub
```{r}
any(is.na(ex$plant_apgfs))
```
```{r, eval=FALSE}
ex.mv.papgfs <- rma.mv(yi = yi,
                     V = vi,
                     random = ~ 1 | exp_ID / obs_ID,
                     data = ex,
                     mods = ~ factor(plant_apgfs) - 1)
```
```{r}
h <- c("Annual/perennial and grass/forb/shrub", "Estimate [95% CI]")
single.mod.cat(ex, "plant_apgfs", ex.mv, ex.mv.papgfs, h)
```



# Plot size (categorical)
```{r}
count(ex, plot)
```
```{r, eval=FALSE}
ex$plotc <- NA
for(i in 1:nrow(ex)) {
  if(is.na(ex$plot[i])) {
    ex$plotc[i] <- "idk"
  } else if(ex$plot[i] < 1) {
    ex$plotc[i] <- "<1"
  } else if(ex$plot[i] == 1) {
    ex$plotc[i] <- "1"
  } else if(between(ex$plot[i], 1.3, 3.75)) {
    ex$plotc[i] <- "1.3-3.75"
  } else if(ex$plot[i] == 4) {
    ex$plotc[i] <- "4"
  } else if(between(ex$plot[i], 6, 9)) {
    ex$plotc[i] <- "6-9"
  } else if(ex$plot[i] == 12) {
    ex$plotc[i] <- "12"
  } else if(between(ex$plot[i], 12.5, 16)) {
    ex$plotc[i] <- "12.5-16"
  } else if(ex$plot[i] == 25) {
    ex$plotc[i] <- "25"
  } else if(between(ex$plot[i], 28, 50)) {
    ex$plotc[i] <- "28-50"
  } else if(ex$plot[i] == 75) {
    ex$plotc[i] <- "75"
  } else {
    ex$plotc[i] <- ">100"
  }
}
ex$plotc <- factor(ex$plotc, 
                           levels = c("<1", "1", "1.3-3.75", "4", "6-9", "12", "12.5-16", 
                                      "25", "28-50", "75", ">100"))
```
```{r}
count(ex, plotc)

any(is.na(ex$plotc))
```
```{r, eval=FALSE}
ex.plotc.na <- ex %>% 
  filter(!is.na(plotc))

ex.mv.plotc <- rma.mv(yi = yi,
                      V = vi,
                      random = ~ 1 | exp_ID / obs_ID,
                      data = ex.plotc.na,
                      mods = ~ factor(plotc) - 1)

ex.mv.plotc.na <- rma.mv(yi = yi,
                         V = vi,
                         random = ~ 1 | exp_ID / obs_ID,
                         data = ex.plotc.na)
```
```{r}
h <- c("Plot size", "Estimate [95% CI]")
single.mod.cat(ex.plotc.na, "plotc", ex.mv.plotc.na, ex.mv.plotc, h)
```



# Seeding of native
## All data
```{r}
count(ex, seeding_native)
```
```{r, eval=FALSE}
ex <- ex %>% 
  mutate(seedn = rep(NA, nrow(ex)))
for(i in 1:nrow(ex)) {
  if(is.na(ex$seeding_native[i])) {
    ex$seedn[i] <- "native seeded"
  } else if(ex$seeding_native[i] == 0) {
    ex$seedn[i] <- "native not seeded"
  } else {
    ex$seedn[i] <- "native seeded"
  }
}
```
```{r}
count(ex, seedn)

any(is.na(ex$seedn))
```
```{r, eval=FALSE}
ex.mv.seedn <- rma.mv(yi = yi,
                      V = vi,
                      random = ~ 1 | exp_ID / obs_ID,
                      data = ex,
                      mods = ~ factor(seedn) - 1)
```
```{r}
h <- c("Seeding of native (all)", "Estimate [95% CI]")
single.mod.cat(ex, "seedn", ex.mv, ex.mv.seedn, h)
```

## Outliers removed
```{r, eval=FALSE}
out.seedn <- NA
ex.seedn.o <- outliers(ex, out.seedn)
ex.mv.seedn.o <- rma.mv(yi = yi,
                       V = vi,
                       random = ~ 1 | exp_ID / obs_ID,
                       data = ex.seedn.o,
                       mods = ~ factor(seedn) - 1)

ex.mv.seedn.na.o <- rma.mv(yi = yi,
                          V = vi,
                          random = ~ 1 | exp_ID / obs_ID,
                          data = ex.seedn.o)
```
```{r}
h <- c("Seeding of native (outliers removed)", "Estimate [95% CI]")
single.mod.cat(ex.seedn.o, "seedn", ex.mv.seedn.na.o, ex.mv.seedn.o, h)
```

