---
title: "Native single moderator models"
author: "Lia Ossanna"
date: "`r format(Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
---
```{r, include=FALSE, message=FALSE}
library(tidyverse)
library(metafor)
load("../RData/nt-1mod.RData")
```

Analysis for Ossanna & Gornish (2022), “Efficacy of labile carbon addition to reduce fast-growing, invasive non-native plants: A review and meta-analysis”, *Journal of Applied Ecology*.

# Introduction
- This is the analysis of the summary effect and effect of a single moderator on native plant abundance.
  - See "Data cleaning and effect size" document for code for data cleaning and calculation of effect size (`pub_data-cleaning.html`).
- For each model there are the model results, proportion of heterogeneity explained by the model ($\frac{Q_M}{Q_E+Q_M}$), and a forest plot.
- When there are missing data for a moderator, a new model is run with the subset of data that the single-moderator model uses; this is reflected in the forest plot.
  - Missing data will return `TRUE` for the first line of code, `any(is.na(dat$variable))`.
- Analysis includes a model run with all the data, and a model run with outliers removed (see "Native outliers for models" document for details; `pub_nt-outliers.html`).
  - When only one model is presented, no outliers were removed.



# Setup
```{r, eval=FALSE}
library(tidyverse)
library(metafor)

# Load data ---------------------------------------------------------------

nt <- read.csv("data/cleaned/native-cleaned.csv") # data cleaning and effect size calculation in separate script

# Functions ---------------------------------------------------------------

single.mod.cat <- function(dat, var, dat.mv, dat.mv.var, h) {
  print(dat.mv.var)
  print(noquote(paste("QM/QT =", dat.mv.var[["QM"]] / sum(dat.mv.var[["QE"]], dat.mv.var[["QM"]]))))
  
  n.forest <- count(dat, !!sym(var))
  colnames(n.forest) <- c("moderator", "n")
  n.forest$end <- rep(")", dim(n.forest)[1])
  n.forest$n <- paste(n.forest$n, n.forest$end, sep = "")
  n.forest$start <- rep("(n = ", dim(n.forest)[1])
  n.forest$n <- paste(n.forest$start, n.forest$n)
  n.forest$var_col <- paste(n.forest$moderator, n.forest$n)
  n.forest <- n.forest %>% 
    filter(!is.na(moderator))
  overall <- paste("Overall (n = ", dat.mv$k, ")", sep = "")
    
  forest(x = c(dat.mv[[1]], dat.mv.var[[1]]),
         ci.lb = c(dat.mv[[6]], dat.mv.var[[6]]),
         ci.ub = c(dat.mv[[7]], dat.mv.var[[7]]),
         slab = c(overall, n.forest$var_col),
         header = h,
         cex = 0.7)
}


outliers <- function(dat, out) {
  dat %>% 
    filter(!obs_ID %in% out)
}

# Outliers ----------------------------------------------------------------

out.cratc <- c(440)
```


# No moderators (summary effect)
```{r, eval=FALSE}
nt.mv <- rma.mv(yi = yi,
                V = vi,
                random = ~ 1 | exp_ID / obs_ID,
                data = nt)
```
```{r}
print(nt.mv)
predict(nt.mv)

# QM/QT
nt.mv[["QM"]] / sum(nt.mv[["QE"]], nt.mv[["QM"]])

# I^2
W <- diag(1 / nt$vi)
X <- model.matrix(nt.mv)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
100 * sum(nt.mv$sigma2) / (sum(nt.mv$sigma2) + (nt.mv$k-nt.mv$p)/sum(diag(P)))

# I^2 across nested experiment and within nested experiment
100 * nt.mv$sigma2 / (sum(nt.mv$sigma2) + (nt.mv$k-nt.mv$p)/sum(diag(P)))

# Probability based on PI (IntHout 2016)
D <- 0 # threshold D (null effect)
M <- nt.mv[["b"]] # summary treatment effect
SD.PI <- predict(nt.mv)$se * sqrt(nt.mv[["k"]]) # SD of prediction interval, calculated from SE

t <- as.numeric((D - M) / (SD.PI))

pt(t, nt.mv[["k"]] - 1, lower.tail = FALSE) # right-tail cumulative t-distribution with k-1 df
```


# Biome
```{r}
any(is.na(nt$biome)) # if FALSE, use nt.mv for no-moderator model
  # but still requires new model for outliers removed, if applicable 
```
```{r, eval=FALSE}
nt.mv.bio <- rma.mv(yi = yi,
                    V = vi,
                    random = ~ 1 | exp_ID / obs_ID,
                    data = nt,
                    mods = ~ factor(biome) - 1)
```
```{r}
h <- c("Biome", "Estimate [95% CI]")
single.mod.cat(nt, "biome", nt.mv, nt.mv.bio, h)
```



# Region
```{r}
any(is.na(nt$region))
```
```{r, eval=FALSE}
nt.mv.reg <- rma.mv(yi = yi,
                    V = vi,
                    random = ~ 1 | exp_ID / obs_ID,
                    data = nt,
                    mods = ~ factor(region) - 1)
```
```{r}
h <- c("Region", "Estimate [95% CI]")
single.mod.cat(nt, "region", nt.mv, nt.mv.reg, h)
```



# Soil suborder
```{r}
any(is.na(nt$soil_suborder)) # if TRUE, run no-moderators model on subset with no missing data for that moderator (i.e. nt.mv.soil.na)
```
```{r, eval=FALSE}
nt.soil.na <- nt %>% 
  filter(!is.na(soil_suborder))

nt.mv.soil <- rma.mv(yi = yi,
                    V = vi,
                    random = ~ 1 | exp_ID / obs_ID,
                    data = nt.soil.na,
                    mods = ~ factor(soil_suborder) - 1)

nt.mv.soil.na <- rma.mv(yi = yi,
                        V = vi,
                        random = ~ 1 | exp_ID / obs_ID,
                        data = nt.soil.na)
```
```{r}
h <- c("Soil suborder", "Estimate [95% CI]")
single.mod.cat(nt, "soil_suborder", nt.mv.soil.na, nt.mv.soil, h)
```



# Duration since first C app (categorical)
```{r}
# Create categories
count(nt, duration_first)
```
```{r, eval=FALSE}
nt$dfc <- NA
for(i in 1:nrow(nt)) {
  if(nt$duration_first[i] == 3) {
    nt$dfc[i] <- "3"
  } else if(between(nt$duration_first[i], 5, 6)) {
    nt$dfc[i] <- "5-6"
  } else if(between(nt$duration_first[i], 7, 12)) {
    nt$dfc[i] <- "7-12"
  } else if(between(nt$duration_first[i], 13, 18)) {
    nt$dfc[i] <- "13-18"
  } else if(between(nt$duration_first[i], 19, 24)) {
    nt$dfc[i] <- "19-24"
  } else if(between(nt$duration_first[i], 25, 36)) {
    nt$dfc[i] <- "25-36"
  } else if(between(nt$duration_first[i], 37, 50)) {
    nt$dfc[i] <- "37-50"
  } else if(between(nt$duration_first[i], 100, 200)) {
    nt$dfc[i] <- "100-200"
  } else {
    nt$dfc[i] <- ">200"
  }
}
nt$dfc <- factor(nt$df, levels = c("3", "5-6", "7-12", "12-18", "19-24", "25-36", "37-50", "100-200", ">200"))
```
```{r}
count(nt, dfc)

any(is.na(nt$dfc))
```
```{r, eval=FALSE}
nt.mv.dfc <- rma.mv(yi = yi,
                    V = vi,
                    random = ~ 1 | exp_ID / obs_ID,
                    data = nt,
                    mods = ~ factor(dfc) - 1)
```
```{r}
h <- c("Duration since first C app", "Estimate [95% CI]")
single.mod.cat(nt, "dfc", nt.mv, nt.mv.dfc, h)
```



# Duration since last C app (categorical)
```{r}
# Create categories
count(nt, duration_last)
```
```{r, eval=FALSE}
nt$dlc <- NA
for(i in 1:nrow(nt)) {
  if(between(nt$duration_last[i], 0, 1.5)) {
    nt$dlc[i] <- "0-1.5"
  } else if(nt$duration_last[i] == 2) {
    nt$dlc[i] <- "2"
  } else if(between(nt$duration_last[i], 3, 3.5)) {
    nt$dlc[i] <- "3-3.5"
  } else if(between(nt$duration_last[i], 4, 6)) {
    nt$dlc[i] <- "4-6"
  } else if(between(nt$duration_last[i], 7, 12)) {
    nt$dlc[i] <- "7-12"
  } else if(between(nt$duration_last[i], 13, 18)) {
    nt$dlc[i] <- "13-18"
  } else if(between(nt$duration_last[i], 19, 24)) {
    nt$dlc[i] <- "19-24"
  } else if(between(nt$duration_last[i], 36, 49)) {
    nt$dlc[i] <- "36-49"
  } else {
    nt$dlc[i] <- ">100"
  }
}
nt$dlc <- factor(nt$dl, levels = c("0-1.5", "2", "3-3.5", "4-6", "7-12", "13-18", "19-24", 
                                   "36-49", ">100"))
```
```{r}
count(nt, dlc)

any(is.na(nt$dlc))
```
```{r, eval=FALSE}
nt.mv.dlc <- rma.mv(yi = yi,
                    V = vi,
                    random = ~ 1 | exp_ID / obs_ID,
                    data = nt,
                    mods = ~ factor(dlc) - 1)
```
```{r}
h <- c("Duration since last C app", "Estimate [95% CI]")
single.mod.cat(nt, "dlc", nt.mv, nt.mv.dlc, h)
```



# C type 
```{r}
any(is.na(nt$C_type))
```
```{r, eval=FALSE}
nt.mv.ctyp <- rma.mv(yi = yi,
                    V = vi,
                    random = ~ 1 | exp_ID / obs_ID,
                    data = nt,
                    mods = ~ factor(C_type) - 1)
```
```{r}
h <- c("C_type", "Estimate [95% CI]")
single.mod.cat(nt, "C_type", nt.mv, nt.mv.ctyp, h)
```


# C rate (categorical)
## All data
```{r}
count(nt, C_rate)
```
```{r, eval=FALSE}
nt$cratc <- NA
for(i in 1:nrow(nt)) {
  if(is.na(nt$C_rate[i])) {
    nt$cratc[i] <- "idk"
  } else if(between(nt$C_rate[i], 0, 100)) {
    nt$cratc[i] <- "30-100"
  } else if(between(nt$C_rate[i], 101, 160)) {
    nt$cratc[i] <- "133-160"
  } else if(between(nt$C_rate[i], 161, 200)) {
    nt$cratc[i] <- "174-200"
  } else if(between(nt$C_rate[i], 201, 300)) {
    nt$cratc[i] <- "210-300"
  } else if(between(nt$C_rate[i], 301, 400)) {
    nt$cratc[i] <- "330-400"
  } else if(between(nt$C_rate[i], 401, 500)) {
    nt$cratc[i] <- "420-500"
  } else if(between(nt$C_rate[i], 501, 600)) {
    nt$cratc[i] <- "506-600"
  } else if(between(nt$C_rate[i], 630, 700)) {
    nt$cratc[i] <- "620-700"
  } else if(between(nt$C_rate[i], 714, 999)) {
    nt$cratc[i] <- "714-999"
  } else if(between(nt$C_rate[i], 1000, 1330)) {
    nt$cratc[i] <- "1000-1330"
  } else if(between(nt$C_rate[i], 1600, 2000)) {
    nt$cratc[i] <- "1600-2000"
  } else if(between(nt$C_rate[i], 2001, 3000)) {
    nt$cratc[i] <- "2110-3000"
  } else if(between(nt$C_rate[i], 3001, 5000)) {
    nt$cratc[i] <- "3346-5000"
  } else {
    nt$cratc[i] <- ">5000"
  }
}
nt$cratc <- factor(nt$cratc, levels = c("30-100", "133-160", "174-200", "210-300", "330-400", "420-500", 
                                        "506-600", "620-700", "714-999", "1000-1330", "1600-2000",
                                        "2110-3000", "3346-5000", ">5000"))
```
```{r}
count(nt, cratc)

any(is.na(nt$cratc))
```
```{r, eval=FALSE}
nt.cratc.na <- nt %>% 
  filter(!is.na(cratc))

nt.mv.cratc <- rma.mv(yi = yi,
                      V = vi,
                      random = ~ 1 | exp_ID / obs_ID,
                      data = nt.cratc.na,
                      mods = ~ factor(cratc) - 1)

nt.mv.cratc.na <- rma.mv(yi = yi,
                         V = vi,
                         random = ~ 1 | exp_ID / obs_ID,
                         data = nt.cratc.na)
```
```{r}
h <- c("C rate (all)", "Estimate [95% CI]")
single.mod.cat(nt.cratc.na, "cratc", nt.mv.cratc.na, nt.mv.cratc, h)
```

## Outliers removed
```{r}
any(is.na(nt$cratc))
```
```{r, eval=FALSE}
nt.cratc.na <- nt %>% 
  filter(!is.na(cratc))

out.cratc <- c(452)
nt.cratc.o <- outliers(nt.cratc.na, nt.out.cratc)

nt.mv.cratc.o <- rma.mv(yi = yi,
                      V = vi,
                      random = ~ 1 | exp_ID / obs_ID,
                      data = nt.cratc.o,
                      mods = ~ factor(cratc) - 1)

nt.mv.cratc.na.o <- rma.mv(yi = yi,
                         V = vi,
                         random = ~ 1 | exp_ID / obs_ID,
                         data = nt.cratc.o)

```
```{r}
h <- c("C rate (out rm)", "Estimate [95% CI]")
single.mod.cat(nt.cratc.o, "cratc", nt.mv.cratc.na.o, nt.mv.cratc.o, h)
```




# C applications total (categorical)
```{r}
# Create categories
count(nt, C_app)
```
```{r, eval=FALSE}
nt$capc <- NA
for(i in 1:nrow(nt)) {
  if(nt$C_app[i] == 1) {
    nt$capc[i] <- "1"
  } else if(nt$C_app[i] == 2) {
    nt$capc[i] <- "2"
  } else if(between(nt$C_app[i], 3, 6)) {
    nt$capc[i] <- "3-6"
  } else if(between(nt$C_app[i], 7, 10)) {
    nt$capc[i] <- "7-10"
  } else if(between(nt$C_app[i], 15, 22)) {
    nt$capc[i] <- "15-22"
  } else if(between(nt$C_app[i], 32, 40)) {
    nt$capc[i] <- "32-40"
  } else {
    nt$capc[i] <- ">40"
  }
}
nt$capc <- factor(nt$capc, levels = c("1", "2", "3-6", "7-10", "15-22", "32-40", ">40")))
```
```{r}
count(nt, capc)

any(is.na(nt$capc))
```
```{r, eval=FALSE}
nt.mv.capc <- rma.mv(yi = yi,
                     V = vi,
                     random = ~ 1 | exp_ID / obs_ID,
                     data = nt,
                     mods = ~ factor(capc) - 1)
```
```{r}
h <- c("C applications", "Estimate [95% CI]")
single.mod.cat(nt, "capc", nt.mv, nt.mv.capc, h)
```




# Months applying C
```{r}
count(nt, C_app_tm)
```
```{r, eval=FALSE}
nt$capt <- NA
for(i in 1:nrow(nt)) {
  if(nt$C_app_tm[i] == 0) {
    nt$capt[i] <- "1 application total"
  } else if(between(nt$C_app_tm[i], 0.001, 6)) {
    nt$capt[i] <- "1-6"
  } else if(between(nt$C_app_tm[i], 7, 12)) {
    nt$capt[i] <- "7-12"
  } else if(between(nt$C_app_tm[i], 13, 24)) {
    nt$capt[i] <- "13-24"
  } else if(between(nt$C_app_tm[i], 25, 36)) {
    nt$capt[i] <- "25-36"
  } else if(between(nt$C_app_tm[i], 37, 48)) {
    nt$capt[i] <- "37-48"
  } else {
    nt$capt[i] <- ">48"
  }
}
nt$capt <- factor(nt$capt, levels = c("1 application total", "1-6", "7-12", "13-24", 
                                      "25-36", "37-48", ">48"))
```
```{r}
count(nt, capt)

any(is.na(nt$capt))
```
```{r, eval=FALSE}
nt.mv.capt <- rma.mv(yi = yi,
                     V = vi,
                     random = ~ 1 | exp_ID / obs_ID,
                     data = nt,
                     mods = ~ factor(capt) - 1)
```
```{r}
h <- c("Months applying C", "Estimate [95% CI]")
single.mod.cat(nt, "capt", nt.mv, nt.mv.capt, h)
```



# Annual/perennial
```{r}
any(is.na(nt$plant_anper))
```
```{r, eval=FALSE}
nt.mv.panp <- rma.mv(yi = yi,
                     V = vi,
                     random = ~ 1 | exp_ID / obs_ID,
                     data = nt,
                     mods = ~ factor(plant_anper) - 1)
```
```{r}
h <- c("Annual/perennial", "Estimate [95% CI]")
single.mod.cat(nt, "plant_anper", nt.mv, nt.mv.panp, h)
```



# Grass/forb/shrub 
```{r}
any(is.na(nt$plant_gfs))
```
```{r, eval=FALSE}
nt.mv.pgfs <- rma.mv(yi = yi,
                     V = vi,
                     random = ~ 1 | exp_ID / obs_ID,
                     data = nt,
                     mods = ~ factor(plant_gfs) - 1)
```
```{r}
h <- c("Grass/forb/shrub", "Estimate [95% CI]")
single.mod.cat(nt, "plant_gfs", nt.mv, nt.mv.pgfs, h)
```



# Annual/perennial and grass/forb/shrub
```{r}
any(is.na(nt$plant_apgfs))
```
```{r, eval=FALSE}
nt.mv.papgfs <- rma.mv(yi = yi,
                     V = vi,
                     random = ~ 1 | exp_ID / obs_ID,
                     data = nt,
                     mods = ~ factor(plant_apgfs) - 1)
```
```{r}
h <- c("Annual/perennial and grass/forb/shrub", "Estimate [95% CI]")
single.mod.cat(nt, "plant_apgfs", nt.mv, nt.mv.papgfs, h)
```


# Plot size (categorical)
```{r}
count(nt, plot)
```
```{r, eval=FALSE}
nt$plotc <- NA
for(i in 1:nrow(nt)) {
  if(is.na(nt$plot[i])) {
    nt$plotc[i] <- "idk"
  } else if(nt$plot[i] < 1) {
    nt$plotc[i] <- "<1"
  } else if(nt$plot[i] == 1) {
    nt$plotc[i] <- "1"
  } else if(between(nt$plot[i], 1.3, 3.75)) {
    nt$plotc[i] <- "1.3-3.75"
  } else if(nt$plot[i] == 4) {
    nt$plotc[i] <- "4"
  } else if(between(nt$plot[i], 6, 9)) {
    nt$plotc[i] <- "6-9"
  } else if(nt$plot[i] == 12) {
    nt$plotc[i] <- "12"
  } else if(between(nt$plot[i], 12.5, 16)) {
    nt$plotc[i] <- "12.5-16"
  } else if(nt$plot[i] == 25) {
    nt$plotc[i] <- "25"
  } else if(between(nt$plot[i], 28, 50)) {
    nt$plotc[i] <- "28-50"
  } else if(nt$plot[i] == 75) {
    nt$plotc[i] <- "75"
  } else {
    nt$plotc[i] <- ">100"
  }
}
nt$plotc <- factor(nt$plotc, 
                           levels = c("<1", "1", "1.3-3.75", "4", "6-9", "12", "12.5-16", 
                                      "25", "28-50", "75", ">100"))
```
```{r}
count(nt, plotc)

any(is.na(nt$plotc))
```
```{r, eval=FALSE}
nt.plotc.na <- nt %>% 
  filter(!is.na(plotc))

nt.mv.plotc <- rma.mv(yi = yi,
                      V = vi,
                      random = ~ 1 | exp_ID / obs_ID,
                      data = nt.plotc.na,
                      mods = ~ factor(plotc) - 1)

nt.mv.plotc.na <- rma.mv(yi = yi,
                         V = vi,
                         random = ~ 1 | exp_ID / obs_ID,
                         data = nt.plotc.na)
```
```{r}
h <- c("Plot size", "Estimate [95% CI]")
single.mod.cat(nt.plotc.na, "plotc", nt.mv.plotc.na, nt.mv.plotc, h)
```



# Seeding of native
```{r}
count(nt, seeding_native)
```
```{r, eval=FALSE}
nt <- nt %>% 
  mutate(seedn = rep(NA, nrow(nt)))
for(i in 1:nrow(nt)) {
  if(is.na(nt$seeding_native[i])) {
    nt$seedn[i] <- "native seeded"
  } else if(nt$seeding_native[i] == 0) {
    nt$seedn[i] <- "native not seeded"
  } else {
    nt$seedn[i] <- "native seeded"
  }
}
```
```{r}
any(is.na(nt$seedn))
```
```{r, eval=FALSE}
nt.mv.seedn <- rma.mv(yi = yi,
                      V = vi,
                      random = ~ 1 | exp_ID / obs_ID,
                      data = nt,
                      mods = ~ factor(seedn) - 1)
```
```{r}
h <- c("Seeding of native", "Estimate [95% CI]")
single.mod.cat(nt, "seedn", nt.mv, nt.mv.seedn, h)
```

