---
title: "Main figures"
author: "Lia Ossanna"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(metafor)
library(orchaRd)
library(ggpubr)

load("../RData/Main-figures.RData")
```

Analysis for Ossanna & Gornish (2022), “Efficacy of labile carbon addition to reduce fast-growing, exotic invasive plants: A review and meta-analysis”, *Journal of Applied Ecology*.

# Introduction
- This document contains the code used to produce the main figures in the paper.
  - See "Data cleaning and effect size" document for code for data cleaning and calculation of effect size (`pub_data-cleaning.html`).

# Setup
```{r, eval=FALSE}
library(tidyverse)
library(metafor)
library(orchaRd)
library(ggpubr)

# Load data ---------------------------------------------------------------

ex <- read.csv("data/cleaned/exotic-cleaned.csv") # data cleaning and effect size calculation in separate script
nt <- read.csv("data/cleaned/native-cleaned.csv")

# Functions ---------------------------------------------------------------

outliers <- function(dat, out) {
  dat %>% 
    filter(!obs_ID %in% out)
}

# Outliers ----------------------------------------------------------------

# Exotic
out <- c(457, 601)
out.cratc <- c(437)

# Native
nt.out.cratc <- c(440)
```

# Figure 1
Figure 1 is an orchard plot to display the results of the exotic and native summary models.
```{r, eval=FALSE}
# Exotic summary model
out <- c(601, 457)
ex.o <- outliers(ex, out)
ex.mv.o <- rma.mv(yi = yi,
                  V = vi,
                  random = ~ 1 | exp_ID / obs_ID,
                  data = ex.o)

# Native summary model
nt.mv <- rma.mv(yi = yi,
                V = vi,
                random = ~ 1 | exp_ID / obs_ID,
                data = nt)

# Table of estimate, CI, and PI
f1.df <- data.frame(model = c("Exotic", "Native"),
                    ci.lb = c(ex.mv.o[["ci.lb"]], nt.mv[["ci.lb"]]),
                    ci.ub = c(ex.mv.o[["ci.ub"]], nt.mv[["ci.ub"]]),
                    pi.lb = c(predict(ex.mv.o)$pi.lb, predict(nt.mv)$pi.lb),
                    pi.ub = c(predict(ex.mv.o)$pi.ub, predict(nt.mv)$pi.ub),
                    estimate = c(ex.mv.o[["b"]], nt.mv[["b"]]))
```
```{r, fig.height=7, fig.width=6}
# Orchard plots
f1.orc.ex <- orchard_plot(ex.mv.o, mod = "Int", xlab = "Effect size (Hedges' g)", transfm = "none") +
  ggtitle("Exotic weed summary response") +
  annotate(geom = "text", x = -10, y = 1.4,
           label = paste0("Confidence interval: ", round(f1.df[1, 2], 3), ", ", round(f1.df[1, 3], 3), "***", "\n",
                          "Prediction interval: ", round(f1.df[1, 4], 3), ", ", round(f1.df[1, 5], 3)),
           hjust = 0)

f1.orc.nt <- orchard_plot(nt.mv, mod = "Int", xlab = "Effect size (Hedges' g)", transfm = "none") +
  ggtitle("Native plant summary response") +
  annotate(geom = "text", x = -10, y = 1.4,
           label = paste0("Confidence interval: ", round(f1.df[2, 2], 3), ", ", round(f1.df[2, 3], 3), "\n",
                          "Prediction interval: ", round(f1.df[2, 4], 3), ", ", round(f1.df[2, 5], 3)),
           hjust = 0)

ggarrange(f1.orc.ex, f1.orc.nt,
          ncol = 1, nrow = 2,
          labels = c("(A)", "(B)"))
```

# Figure 2
Figure 2 is a forest plot of exotic weed response by plant lifeform (annual/perennial and grass/forb/shrub).
```{r, eval=FALSE}
# Exotic anpergfs model
ex.mv.papgfs <- rma.mv(yi = yi,
                       V = vi,
                       random = ~ 1 | exp_ID / obs_ID,
                       data = ex,
                       mods = ~ factor(plant_apgfs) - 1)

# Table of estimate, CI, and PI
n.forest.ex.papgfs <- count(ex, !!sym("plant_apgfs"))
n.forest.ex.papgfs$x <- ex.mv.papgfs[[1]]
n.forest.ex.papgfs$ci.lb <- ex.mv.papgfs[[6]]
n.forest.ex.papgfs$ci.ub <- ex.mv.papgfs[[7]]
n.forest.ex.papgfs <- n.forest.ex.papgfs %>% 
  filter(plant_apgfs %in% c("annual forb", "annual graminoid", 
                            "perennial forb", "perennial graminoid"))
```
```{r, fig.height=4, fig.width=6}
# Forest plot
forest(x = n.forest.ex.papgfs$x,
       ci.lb = n.forest.ex.papgfs$ci.lb,
       ci.ub = n.forest.ex.papgfs$ci.ub,
       slab = n.forest.ex.papgfs$plant_apgfs,
       header = "Lifeform",
       annotate = FALSE,
       xlab = substitute(paste("Effect size (Hedges' ", italic("g"), ")")),
       ilab = n.forest.ex.papgfs$n,
       ilab.xpos = -1.3,
       cex = 0.75, 
       top = 2)

par(cex = 0.75, font = 4)
text(x = -1.3, y = 6, labels = "k")
par(cex = 0.75, font = 2)
text(x = 0, y = 6, labels = "Exotic weed response")
```

# Figure 3
Figure 3 is a forest plot of exotic weed response by study duration (months from first C app to harvest).
```{r, eval=FALSE}
# Exotic dlc model
ex.mv.dlc <- rma.mv(yi = yi,
                    V = vi,
                    random = ~ 1 | exp_ID / obs_ID,
                    data = ex,
                    mods = ~ factor(dlc) - 1)

# Table of estimate, CI, and PI
n.forest.ex.dlc <- count(ex, !!sym("dlc"))
n.forest.ex.dlc$x <- ex.mv.dlc[[1]]
n.forest.ex.dlc$ci.lb <- ex.mv.dlc[[6]]
n.forest.ex.dlc$ci.ub <- ex.mv.dlc[[7]]
```
```{r, fig.height=4, fig.width=6}
forest(x = n.forest.ex.dlc$x,
       ci.lb = n.forest.ex.dlc$ci.lb,
       ci.ub = n.forest.ex.dlc$ci.ub,
       slab = n.forest.ex.dlc$dlc,
       header = "Study duration (months)",
       annotate = FALSE,
       xlab = substitute(paste("Effect size (Hedges' ", italic("g"), ")")),
       ilab = n.forest.ex.dlc$n,
       ilab.xpos = -2.4,
       cex = 0.75,
       top = 2)

par(cex = 0.75, font = 4)
text(x = -2.4, y = 11, labels = "k")
par(cex = 0.75, font = 2)
text(x = 0, y = 11, labels = "Exotic weed response")
```

# Figure 4
Figure 4 is a forest plot of exotic weed response by C application rate.
```{r, eval=FALSE}
# Exotic C rate models
ex.cratc.na <- ex %>% 
  filter(!is.na(cratc)) # some C rates are missing or couldn't be converted to g C/m2
ex.cratc.o <- outliers(ex.cratc.na, out.cratc) # remove outliers

ex.mv.cratc.o <- rma.mv(yi = yi,
                        V = vi,
                        random = ~ 1 | exp_ID / obs_ID,
                        data = ex.cratc.o,
                        mods = ~ factor(cratc) - 1) # summary model using subset of observations with C rate

ex.mv.cratc.na.o <- rma.mv(yi = yi,
                           V = vi,
                           random = ~ 1 | exp_ID / obs_ID,
                           data = ex.cratc.o) # model with C rate as a moderator

# Table of estimate, CI, and PI
n.forest.ex.cratc <- count(ex.cratc.o, !!sym("cratc"))
n.forest.ex.cratc$x <- ex.mv.cratc.o[[1]]
n.forest.ex.cratc$ci.lb <- ex.mv.cratc.o[[6]]
n.forest.ex.cratc$ci.ub <- ex.mv.cratc.o[[7]]
```
```{r, fig.height=4, fig.width=4}
forest(x = n.forest.ex.cratc$x,
       ci.lb = n.forest.ex.cratc$ci.lb,
       ci.ub = n.forest.ex.cratc$ci.ub,
       slab = n.forest.ex.cratc$cratc,
       annotate = FALSE,
       header = "C rate",
       xlab = substitute(paste("Effect size (Hedges' ", italic("g"), ")")),
       ilab = n.forest.ex.cratc$n,
       ilab.xpos = -5,
       cex = 0.75,
       top = 2)

par(cex = 0.65, font = 1)
text(x = -6.35, y = 16.1, labels = bquote(paste("(g C ", m^-2, " ", y^-1, ")")),)
par(cex = 0.75, font = 4)
text(x = -4.7, y = 16.1, labels = "k")
par(cex = 0.75, font = 2)
text(x = 0, y = 16.1, labels = "Exotic weed response")
```

# Figure 5
Figure 5 is a forest plot of native plant response by C rate.
```{r, eval=FALSE}
# Native C rate models
nt.cratc.na <- nt %>% 
  filter(!is.na(cratc)) # some C rates are missing or couldn't be converted to g C/m2
nt.cratc.o <- outliers(nt.cratc.na, nt.out.cratc) # remove outliers

ex.mv.cratc.o <- rma.mv(yi = yi,
                        V = vi,
                        random = ~ 1 | exp_ID / obs_ID,
                        data = ex.cratc.o,
                        mods = ~ factor(cratc) - 1) # summary model using subset of observations with C rate

nt.mv.cratc.o <- rma.mv(yi = yi,
                        V = vi,
                        random = ~ 1 | exp_ID / obs_ID,
                        data = nt.cratc.o,
                        mods = ~ factor(cratc) - 1) # model with C rate as a moderator

# Table of estimate, CI, and PI
n.forest.nt.cratc <- count(nt.cratc.o, !!sym("cratc"))
n.forest.nt.cratc$x <- nt.mv.cratc.o[[1]]
n.forest.nt.cratc$ci.lb <- nt.mv.cratc.o[[6]]
n.forest.nt.cratc$ci.ub <- nt.mv.cratc.o[[7]]
```
```{r, fig.height=4, fig.width=4}
forest(x = n.forest.nt.cratc$x,
       ci.lb = n.forest.nt.cratc$ci.lb,
       ci.ub = n.forest.nt.cratc$ci.ub,
       slab = n.forest.nt.cratc$cratc,
       header = "C rate",
       annotate = FALSE,
       xlab = substitute(paste("Effect size (Hedges' ", italic("g"), ")")),
       ilab = n.forest.nt.cratc$n,
       ilab.xpos = -2.5,
       cex = 0.75,
       top = 2)

par(cex = 0.65, font = 1)
text(x = -3.43, y = 16.1, labels = bquote(paste("(g C ", m^-2, " ", y^-1, ")")),)
par(cex = 0.75, font = 4)
text(x = -2.3, y = 16.1, labels = "k")
par(cex = 0.75, font = 2)
text(x = 0, y = 16.1, labels = "Native plant response")
```

