---
title: "Native model selection"
author: "Lia Ossanna"
date: "`r format(Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
options(knitr.kable.NA = "")
library(kableExtra)
library(tidyverse)
library(metafor)
library(glmulti)
eval(metafor:::.glmulti)
load("../RData/nt-mod14o.RData")
```

Analysis for Ossanna & Gornish (2022), “Efficacy of labile carbon addition to reduce fast-growing, invasive non-native plants: A review and meta-analysis”, *Journal of Applied Ecology*.

# Introduction
- Model selection follows [this tutorial](https://www.metafor-project.org/doku.php/tips:model_selection_with_glmulti_and_mumin) from the  `metafor` website.
  - Code also adapted from Kinlock 2017 (*Global Ecology and Biogeography*) and Yan 2018 (*Forests*).
- See "Non-native (exotic) model selection" document (`pub_ex-modsel.html`) for rationale of moderators included.
- See "Data cleaning and effect size" document for code for data cleaning and calculation of effect size (`pub_data-cleaning.html`).



# Setup
```{r, eval=FALSE}
library(tidyverse)
library(metafor)
library(glmulti)

# Load data ---------------------------------------------------------------

nt <- read.csv("data/cleaned/native-cleaned.csv") # data cleaning and effect size calculation in separate script

# Model selection setup ---------------------------------------------------

rma.glmulti <- function(formula, data, V, random,...) {
  do.call("rma.mv", list(as.formula(paste(deparse(formula))), V = as.name(V), random = as.name(random), data = data,  method = "ML", ...))
}
rand <- list(~ 1 | obs_ID, ~ 1 | exp_ID)

# Multimodel inference
eval(metafor:::.glmulti)
```



# Model: `region`, `dlc`, `C_type`, `cratc`, `capt`, `plant_apgfs`, `plotc`
- Model had two outliers removed.

```{r, eval=FALSE}
nt.ms14.o <- nt.ms14 %>% 
  filter(obs_ID != 1697) %>% 
  filter(obs_ID != 1002)

res14.o.nt <- glmulti(yi ~ region + dlc + C_type + cratc + capt + plant_apgfs + plotc, 
                    V = "vi", data = nt.ms14.o, level = 1, fitfunction = rma.glmulti, 
                    random = "rand", crit = "aicc")
```
```{r}
print(res14.o.nt)

# Models within 2 AICc units
top <- weightable(res14.o.nt)
top <- top[top$aicc <= min(top$aicc) + 2, ]
top 
plot(res14.o.nt, type = "s")

# Top 5 models
weightable(res14.o.nt)[1:5, ]
```

## Top model 1
```{r, fig.width=7, fig.height=7}
summary(res14.o.nt@objects[[1]])

forest(x = res14.o.nt@objects[[1]]$b,
       ci.lb = res14.o.nt@objects[[1]]$ci.lb,
       ci.ub = res14.o.nt@objects[[1]]$ci.ub,
       slab = rownames(res14.o.nt@objects[[1]]$b),
       alim = c(-5, 5),
       header = c("Top model 1", "Estimate [95% CI]"),
       cex = 0.75)
```



# Multimodel inference
- Multimodel inference is not necessary because there is only 1 top model (no others within 2 AICc units).