---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 9, fig.height = 11)
library(kableExtra)

load("../RData/systematic-review.RData")
load("../RData/2022-01_results.RData")

library(tidyverse)
library(readxl)
library(metafor)
```

# Supplemental materials
Supplemental materials for Ossanna & Gornish (2022), "Efficacy of labile carbon addition to reduce fast-growing, exotic invasive plants: A review and meta-analysis". \

**Table S1 & S2. Raw data**  
For Tables S1 & S2, see accompanying Zenodo archive under the same name as the paper title. The Zenodo archive also includes R Markdown documents detailing analysis and code. \
  
**Table S3. Systematic review: Publication types** 
```{r}
peer$perc <- round(peer$perc, 1)
peer$peer <- c("conference", "doctoral dissertation", "peer-reviewed article", "technical report", "master's thesis")
colnames(peer) <- c("Publication type", "n", "Percent (%)")
peer %>%
  arrange(desc(n)) %>% 
  kbl(booktabs = TRUE) %>%
  kable_classic(full_width = FALSE, latex_options = "HOLD_position")
```

\

**Table S4. Systematic review: Study regions**
```{r}
reg$perc <- round(reg$perc, 1)
colnames(reg) <- c("Region", "n", "Percent (%)")
reg %>%
  arrange(desc(n)) %>% 
  kbl(booktabs = TRUE) %>%
  kable_classic(full_width = FALSE, latex_options = "HOLD_position")
```

```{r, fig.height=5}
hist(review$dur, breaks = 50, xlab = "Study duration (months)", main = NULL)
```
**Figure S1.** Study duration for systematic review, where study duration is defined as months from the first C application to the last plant measurements.

```{r, fig.height=5}
hist(plot.na$plot, breaks = 50, xlab = expression(paste("Plot size (m"^2*")")), main = NULL)
```
**Figure S2.** Plot size for systematic review.

\newpage 
**Table S5. Systematic review: C types**
```{r}
ctypa$perc <- round(ctypa$perc, 1)
colnames(ctypa) <- c("C type", "n", "Percent (%)")
ctypa %>%
  arrange(desc(n)) %>% 
  kbl(booktabs = TRUE) %>%
  kable_classic(full_width = FALSE, latex_options = "HOLD_position")
```

```{r, fig.height=5}
hist(cratav.na$cratav, breaks = 50, xlab = expression(paste("C rate (g C m"^-2*" y"^-1*")")), main = NULL)
```
**Figure S3.** Average C rate for systematic review. \

\

**Table S6.** Systematic review: Number of treatment combinations with C addition
```{r}
mtrtn$perc <- round(mtrtn$perc, 1)
mtrtn$mtrtn <- c("C addition only", "1 additional treatment", "2 additional treatments", "3 additional treatments")
colnames(mtrtn) <- c("Number of additional treatments", "n", "Percent (%)")
mtrtn %>%
  arrange(desc(n)) %>% 
  kbl(booktabs = TRUE) %>%
  kable_classic(full_width = FALSE, latex_options = "HOLD_position")
```

\newpage
**Table S7. Systematic review: Types of treatment combinations with C addition** 
```{r}
mtrt$perc <- round(mtrt$perc, 1)
colnames(mtrt) <- c("Additional treatments", "n", "Percent (%)")
mtrt %>%
  arrange(desc(n)) %>% 
  kbl(booktabs = TRUE) %>%
  kable_classic(full_width = FALSE, latex_options = "HOLD_position")
```

\

**Table S8. Systematic review: Inclusion of cost** 
```{r}
cost$perc <- round(cost$perc, 1)
cost$cost <- c("absent", "discussed in context of results", "mentioned briefly", "quantitative estimate")
colnames(cost) <- c("Cost inclusion", "n", "Percent (%)")
cost %>%
  arrange(desc(n)) %>% 
  kbl(booktabs = TRUE) %>%
  kable_classic(full_width = FALSE, latex_options = "HOLD_position")
```



```{r}
par(mfcol = c(2, 1))
h <- c("[A] Duration since first application (exotic)", "Estimate [95% CI]")
forest.cat(ex.dfc.o, "dfc", ex.mv.dfc.na.o, ex.mv.dfc.o, h)
h <- c("[B] Duration since first application (native)", "Estimate [95% CI]")
forest.cat(nt, "dfc", nt.mv, nt.mv.dfc, h)
```
**Figure S4.** Standardized mean Hedges’ *g* effect size $\pm$ 95% confidence interval (CI) for exotic (A) and native plant abundance (B) in response to C addition, categorized by study duration (months from first C application to when first plant measurements taken). CIs that do not overlap zero are considered significant.

```{r}
par(mfcol = c(2, 1))
h <- c("[A] Duration since last application (exotic)", "Estimate [95% CI]")
forest.cat(ex, "dlc", ex.mv.o, ex.mv.dlc, h)
h <- c("[B] Duration since last application (native)", "Estimate [95% CI]")
forest.cat(nt, "dlc", nt.mv, nt.mv.dlc, h)
```
**Figure S5.** Standardized mean Hedges’ *g* effect size $\pm$ 95% confidence interval (CI) for exotic (A) and native plant abundance (B) in response to C addition, categorized by study duration (months from first C application to when last plant measurements taken), with number of comparisons *k*. CIs that do not overlap zero are considered significant.

```{r}
par(mfcol = c(2, 1))
h <- c("[A] Annual/perennial and grass/forb/shrub (exotic)", "Estimate [95% CI]")
forest.cat(ex, "plant_apgfs", ex.mv.o, ex.mv.papgfs, h)
h <- c("[B] Annual/perennial and grass/forb/shrub (native)", "Estimate [95% CI]")
forest.cat(nt, "plant_apgfs", nt.mv, nt.mv.papgfs, h)
```
**Figure S6.** Standardized mean Hedges’ *g* effect size $\pm$ 95% confidence interval (CI) for exotic (A) and native plant abundance (B) in response to C addition, categorized by plant lifeform and duration (annual/perennial and grass/forb/shrub), with number of comparisons *k*. CIs that do not overlap zero are considered significant.

```{r}
par(mfcol = c(2, 1))
h <- c("[A] Annual/perennial (exotic)", "Estimate [95% CI]")
forest.cat(ex, "plant_anper", ex.mv.o, ex.mv.panp, h)
h <- c("[B] Annual/perennial (native)", "Estimate [95% CI]")
forest.cat(nt, "plant_anper", nt.mv, nt.mv.panp, h)
```
**Figure S7.** Standardized mean Hedges’ *g* effect size $\pm$ 95% confidence interval (CI) for exotic (A) and native plant abundance (B) in response to C addition, categorized by plant duration (annual/perennial), with number of comparisons *k*. CIs that do not overlap zero are considered significant.

```{r}
par(mfcol = c(2, 1))
h <- c("[A] Grass/forb/shrub (exotic)", "Estimate [95% CI]")
forest.cat(ex, "plant_gfs", ex.mv.o, ex.mv.pgfs, h)
h <- c("[B] Grass/forb/shrub (native)", "Estimate [95% CI]")
forest.cat(nt, "plant_gfs", nt.mv, nt.mv.pgfs, h)
```
**Figure S8.** Standardized mean Hedges’ *g* effect size $\pm$ 95% confidence interval (CI) for exotic (A) and native plant abundance (B) in response to C addition, categorized by plant lifeform (grass/forb/shrub), with number of comparisons *k*. CIs that do not overlap zero are considered significant.

```{r}
par(mfcol = c(2, 1))
h <- c("[A] C type (exotic)", "Estimate [95% CI]")
forest.cat(ex, "C_type", ex.mv.o, ex.mv.ctyp, h)
h <- c("[B] C type (native)", "Estimate [95% CI]")
forest.cat(nt, "C_type", nt.mv, nt.mv.ctyp, h)
```
**Figure S9.** Standardized mean Hedges’ *g* effect size $\pm$ 95% confidence interval (CI) for exotic (A) and native plant abundance (B) in response to C addition, categorized by C type, with number of comparisons *k*. CIs that do not overlap zero are considered significant.

```{r}
par(mfcol = c(2, 1))
h <- c("[A] C rate (exotic)", "Estimate [95% CI]")
forest.cat(ex.cratc.o, "cratc", ex.mv.cratc.na.o, ex.mv.cratc.o, h)
h <- c("[B] C rate (native)", "Estimate [95% CI]")
forest.cat(nt.cratc.o, "cratc", nt.mv.cratc.na.o, nt.mv.cratc.o, h)
```
**Figure S10.** Standardized mean Hedges’ *g* effect size $\pm$ 95% confidence interval (CI) for exotic (A) and native plant abundance (B) in response to C addition, categorized by C rate (g C m^-2^ y^-1^), with number of comparisons *k*. CIs that do not overlap zero are considered significant.

```{r}
par(mfcol = c(2, 1))
h <- c("[A] C applications (exotic)", "Estimate [95% CI]")
forest.cat(ex, "capc", ex.mv.o, ex.mv.capc, h)
h <- c("[B] C applications (native)", "Estimate [95% CI]")
forest.cat(nt, "capc", nt.mv, nt.mv.capc, h)
```
**Figure S11.** Standardized mean Hedges’ *g* effect size $\pm$ 95% confidence interval (CI) for exotic (A) and native plant abundance (B) in response to C addition, categorized by total number of C applications, with number of comparisons *k*. CIs that do not overlap zero are considered significant.

```{r}
par(mfcol = c(2, 1))
h <- c("[A] Months applying C (exotic)", "Estimate [95% CI]")
forest.cat(ex, "capt", ex.mv.o, ex.mv.capt, h)
h <- c("[B] Months applying C (native)", "Estimate [95% CI]")
forest.cat(nt, "capt", nt.mv, nt.mv.capt, h)
```
**Figure S12.** Standardized mean Hedges’ *g* effect size $\pm$ 95% confidence interval (CI) for exotic (A) and native plant abundance (B) in response to C addition, categorized by number of months applying C (takes into account reapplication and study duration), with number of comparisons *k*. CIs that do not overlap zero are considered significant.

```{r}
par(mfcol = c(2, 1))
h <- c("[A] Region (exotic)", "Estimate [95% CI]")
forest.cat(ex.reg.o, "region", ex.mv.reg.na.o, ex.mv.reg.o, h)
h <- c("[B] Region (native)", "Estimate [95% CI]")
forest.cat(nt, "region", nt.mv, nt.mv.reg, h)
```
**Figure S13.** Standardized mean Hedges’ *g* effect size $\pm$ 95% confidence interval (CI) for exotic (A) and native plant abundance (B) in response to C addition, categorized by study region, with number of comparisons *k*. CIs that do not overlap zero are considered significant.

```{r}
par(mfcol = c(2, 1))
h <- c("[A] Plot size (exotic)", "Estimate [95% CI]")
forest.cat(ex.plotc.na, "plotc", ex.mv.plotc.na, ex.mv.plotc, h)
h <- c("[B] Plot size (native)", "Estimate [95% CI]")
forest.cat(nt.plotc.na, "plotc", nt.mv.plotc.na, nt.mv.plotc, h)
```
**Figure S14.** Standardized mean Hedges’ *g* effect size $\pm$ 95% confidence interval (CI) for exotic (A) and native plant abundance (B) in response to C addition, categorized by plot size (m^2^), with number of comparisons *k*. CIs that do not overlap zero are considered significant.

```{r}
par(mfcol = c(2, 1))
h <- c("[A] Seeding of native (exotic)", "Estimate [95% CI]")
forest.cat(ex.seedn.o, "seedn", ex.mv.seedn.na.o, ex.mv.seedn.o, h)
h <- c("[B] Seeding of native (native)", "Estimate [95% CI]")
forest.cat(nt, "seedn", nt.mv, nt.mv.seedn, h)
```
**Figure S15.** Standardized mean Hedges’ *g* effect size $\pm$ 95% confidence interval (CI) for exotic (A) and native plant abundance (B) in response to C addition, categorized by seeding of native plant species (seeded/not seeded), with number of comparisons *k*. CIs that do not overlap zero are considered significant.




\newpage
**Table S9. Meta-analysis: Heterogeneity statistics**
```{r}
hetero %>% 
  kbl(longtable = TRUE, booktabs = TRUE) %>% 
  kable_styling(latex_options = c("HOLD_position", "striped",
                                                 "repeat_header")) %>% 
  pack_rows("Summary", 1, 2) %>%
  pack_rows("Region", 3, 4) %>% 
  pack_rows("Duration since first C app", 5, 6) %>% 
  pack_rows("Duration since last C app", 7, 8) %>% 
  pack_rows("C type", 9, 10) %>% 
  pack_rows("C rate", 11, 12) %>% 
  pack_rows("Total C applications", 13, 14) %>% 
  pack_rows("Months applying C", 15, 16) %>% 
  pack_rows("Grass/forb/shrub", 17, 18) %>% 
  pack_rows("Annual/perennial", 19, 20) %>% 
  pack_rows("Annual/perennial and grass/forb/shrub", 21, 22) %>% 
  pack_rows("Plot size", 23, 24) %>% 
  pack_rows("Seeding of native", 25, 26)
```

*QE*, unexplained heterogeneity (dispersion); *QE_df*, corresponding degrees of freedom; *QE_p*, corresponding p-value; *QM*, heterogeneity explained by the model; *QM_df*, corresponding degrees of freedom; *QM_p*, corresponding p-value; *QM/QT*, proportion of observed (total) heterogeneity explained by the model.