---
title: "Systematic review"
author: "Lia Ossanna"
date: "11/23/2021"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "..")
```


# Introduction
- This systematic review is to survey what types of experiments have been done using C addition. 
  - It only looks at experimental setup and conditions and no results (to avoid a vote count). 
- This includes 83 papers in total, which are not divided up as "experiments" by study location like the meta-analysis (each given an `exp_ID`).
  - 47 papers were included in both the review and the meta-analysis.
    - 1 paper was not included in the review but was included in the meta-analysis (Haubensak 2004). This is because it is the same study from Haubensak 2006, but both papers provided data for the meta-analysis. This is a unique situation.
  - 21 papers were included in the review and not the meta-analysis because they lacked reports of variance (SD or SE). 
  - 13 papers were included in the review and not the meta-analysis because they were not statistically suitable for the meta-analysis (lacked 3 true replicates in the same location; reported data pooled across years or treatments).
  - 2 papers were included in the review and not the meta-analysis because they did not measure biomass, density, or cover of plants.
- Only simple analysis has been done to find the percentage of studies for each level of relevant categorical variables, or averages for continuous variables. Values in the summary section are rounded to the nearest whole percent.


# Summary
- 73% of papers were of studies conducted in the USA.
  - This distribution is terribly biased, and there is only 1 paper for the entire continent of Asia and 2 for Africa and no representation from South America.
- Median study duration (of longest study duration possible, based on experimental setup) was 20 months.
  - This generally captures about 2-3 growing seasons.
- 51% of papers used sucrose for C application, but sucrose is generally noted as one of the more expensive C types.
- Median C rate was 420 g C m^-2^.
  - This translates to about 1000 g m^-2^ sucrose, or about 900 g m^-2^ sawdust (although this conversion varies).
- 83% of papers tested a single C application rate.
- 70% of papers applied C more than once (although this might not be feasible or likely for land managers, it's still good to see the effects of reapplication).
- 37% of papers tested only C application; 40% of papers tested 1 other management strategy in conjunction with C application; 18% of papers tested 2 other management strategies; 5% tested 3 management strategies.
  - I was kind of surprised that the majority of studies were looking at effects of multiple treatments, so maybe my assertion that people aren't looking at that enough is wrong.
  - It's still difficult to use meta-analytic methods to summarize the effects, though.
- Of the papers that tested multiple treatments with C addition, 29% tested seeding native species; 24% tested burning; 11% tilling (or ground disturbance); 9% tested water manipulation.
  - In absolute terms (out of all the papers), this translates to: 16% tested seeding native species; 13% tested burning; 6% tilling (or ground disturbance); 5% tested water manipulation.
- 61% of papers made no mention of cost; 22% made a brief mention of cost (no more than a couple sentences); 11% discussed cost at greater length, and with relation to their study results; 6% gave actual numbers or attempted some kind of quantitative estimate of cost.
- Median plot size was 4 m^2^.
- 76% of papers came from peer-reviewed journals; 17% were masters theses or doctoral dissertations.


# Setup
```{r, message=FALSE}
library(readxl)
library(tidyverse)

# Load data ---------------------------------------------------------------

review <- read_xlsx("C-addition-studies.xlsx", sheet = "screen_review")
```

# Biome
- Honestly, `biome` has always been a little sketchy because authors report grassland types in different ways sometimes and I can't always recognize what is the same thing, unlike grouping things together by `region`, which I definitely can do.
```{r}
bio <- review %>%
  filter(!is.na(biome)) %>% 
  count(biome)
bio <- bio %>% 
  mutate(perc = n / sum(bio$n) * 100)

bio
```


# Region
```{r}
reg <- review %>%
  filter(!is.na(region)) %>% 
  count(region)
reg <- reg %>% 
  mutate(perc = n / sum(reg$n) * 100)
reg

# Just USA
reg.usa <- reg %>% 
  filter(str_detect(region, "USA"))
sum(reg.usa$n)
sum(reg.usa$perc)
```


# Study duration
- Longest possible time range from when C was first applied to when measurements were last taken to capture maximum study duration, since many restoration studies are not generally long enough.
```{r}
summary(review$dur, na.rm = TRUE)
hist(review$dur, breaks = 40)

# To better see first part of histogram
dur.majority <- review %>% 
  filter(dur < 60)
hist(dur.majority$dur, breaks = 20)
```


# C type
- Honestly the code it took to get a proper count of C types tested because some studies tested multiple types of C (in different treatments) is terrible because I just had to make multiple columns for each treatment in the spreadsheet, which doesn't seem like a very good method, but I didn't know what else to do (same for multiple treatments).  

## Types
```{r}
# This whole thing is a terrible example of code
# Combine counts of studies that tested multiple C types
ctypa.s <- review %>%
  filter(ctypm == "single") %>% 
  count(ctyp1)

ctypa.m <- review %>%
  filter(ctypm == "multiple") %>% 
  select(ctyp2, ctyp3, ctyp4) %>% 
  pivot_longer(everything(), names_to = "col", values_to = "ctyp1") %>% 
  filter(!is.na(ctyp1)) %>% 
  select(ctyp1) %>% 
  count(ctyp1)

ctypa.int <- intersect(ctypa.s$ctyp1, ctypa.m$ctyp1)
ctypa.add.s <- ctypa.s %>% 
  filter(ctyp1 %in% ctypa.int) %>% 
  select(order(colnames(.)))
ctypa.add.m <- ctypa.m %>% 
  filter(ctyp1 %in% ctypa.int) %>% 
  select(order(colnames(.))) %>% 
  mutate(n2 = ctypa.add.s$n) %>% 
  select(-ctyp1) %>% 
  mutate(n = n + n2) %>% 
  select(-n2)
ctypa.add.s <- ctypa.add.s[ , -2]
ctypa.add.s <- cbind(ctypa.add.s, ctypa.add.m)

ctypa.s <- ctypa.s %>% 
  filter(!ctyp1 %in% ctypa.int)
ctypa <- rbind(ctypa.add.s, ctypa.s)

rm(ctypa.add.m, ctypa.add.s, ctypa.m, ctypa.s, ctypa.int)

# Percentages
ctypa <- ctypa %>% 
  mutate(perc = n / sum(ctypa$n) * 100)
ctypa
```

## Number of types
```{r}
ctypm <- review %>%
  filter(!is.na(ctypm)) %>% 
  count(ctypm)
ctypm.sum <- sum(ctypm["n"])
ctypm <- ctypm %>% 
  mutate(perc = n / ctypm.sum * 100)
ctypm
```


# C rate
Averaged when paper tested multiple C rates.
```{r}
cratav.na <- review %>% 
  filter(!is.na(cratav))
summary(cratav.na$cratav)
hist(cratav.na$cratav, breaks = 40)

# To better see first part of histogram
cratav.majority <- cratav.na %>% 
  filter(cratav < 1000)
hist(cratav.majority$cratav, breaks = 30)
```

Percent of papers that tested multiple C rates:
```{r}
cratm <- review %>%
  filter(!is.na(cratm)) %>% 
  count(cratm)
cratm.sum <- sum(cratm["n"])
cratm <- cratm %>% 
  mutate(perc = n / cratm.sum * 100)

cratm[10, ]
```


# Reapplication (yes/no)
- It's kind of hard to figure out exactly how many applications studies do, so to save time I just did a yes/no count.
```{r}
capr <- review %>%
  filter(!is.na(capr)) %>% 
  count(capr)
capr.sum <- sum(capr["n"])
capr <- capr %>% 
  mutate(perc = n / capr.sum * 100)
capr
```


# Multiple treatments
## Treatment types (relative)
```{r}
# This is what I did for C type and it's still terrible
# Combine counts of studies that tested multiple treatments
mtrt.s <- review %>%
  filter(mtrtn == 1) %>% 
  count(mtrt1)

mtrt.m <- review %>%
  filter(mtrtn != 1) %>% 
  select(mtrt2, mtrt3) %>% 
  pivot_longer(everything(), names_to = "col", values_to = "mtrt1") %>% 
  filter(!is.na(mtrt1)) %>% 
  select(mtrt1) %>% 
  count(mtrt1)

mtrt.int <- intersect(mtrt.s$mtrt1, mtrt.m$mtrt1)
mtrt.add.s <- mtrt.s %>% 
  filter(mtrt1 %in% mtrt.int) %>% 
  select(order(colnames(.)))
mtrt.add.m <- mtrt.m %>% 
  filter(mtrt1 %in% mtrt.int) %>% 
  select(order(colnames(.))) %>% 
  mutate(n2 = mtrt.add.s$n) %>% 
  select(-mtrt1) %>% 
  mutate(n = n + n2) %>% 
  select(-n2)
mtrt.add.s <- mtrt.add.s[ , -2]
mtrt.add.s <- cbind(mtrt.add.s, mtrt.add.m)

mtrt.s <- mtrt.s %>% 
  filter(!mtrt1 %in% mtrt.int)
mtrt <- rbind(mtrt.add.s, mtrt.s)

rm(mtrt.add.m, mtrt.add.s, mtrt.m, mtrt.s, mtrt.int)

mtrt <- mtrt %>% 
  mutate(perc = n / sum(mtrt$n) * 100)
mtrt
```

## Treatment types (absolute)
```{r}
mtrt.absolute <- mtrt %>% 
  mutate(perc = n / dim(review)[1] * 100)
mtrt.absolute
```


## Number of multiple/additional treatments
```{r}
mtrtn <- review %>%
  filter(!is.na(mtrtn)) %>% 
  count(mtrtn)
mtrtn.sum <- sum(mtrtn["n"])
mtrtn <- mtrtn %>% 
  mutate(perc = n / mtrtn.sum * 100)
mtrtn
```

# Cost
```{r}
cost <- review %>%
  filter(!is.na(cost)) %>% 
  count(cost)
cost.sum <- sum(cost["n"])
cost <- cost %>% 
  mutate(perc = n / cost.sum * 100)
cost
```

# Plot size
```{r}
plot.na <- review %>% 
  filter(!str_detect(plot, "not")) %>% 
  mutate(plot = round(as.numeric(plot), 2))
summary(plot.na$plot)
hist(plot.na$plot, breaks = 30)

# To better see first part of histogram
plot.majority <- plot.na %>% 
  filter(plot < 30)
hist(plot.majority$plot, breaks = 20)
```


# Peer review
```{r}
peer <- review %>%
  count(peer)
peer.sum <- sum(peer["n"])
peer <- peer %>% 
  mutate(perc = n / peer.sum * 100)
peer
```

